---
title: "hurdle"
author: "anne"
date: "3 desember 2018"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

load("processdata/browse_9.rda")
# load("processdata/browse9pos.rda")

```



## Christer's approach

```{r}
m1 <- glm(cbind(bt.binom, beitetrykk) ~ distvei1 + disthus + landsdel + skogkategori + kant + helling + hohkatb + treartgruppe, family = "binomial", data = browse9) # not the right variables in the response, should be: "beitet, totaltundersokt"

summary(m1)
plot(m1)
```




## Hurdle model (Also: two-way model) and two-way model "old school" (Zuur 2009, chapter: Zero-truncated and zero-inflated models for count data)
For count data, helps with excess zeros and overdispersion

##### Hurdle model, using hurdle() from pscl package
```{r}

f1 <- formula(beitetrykkr ~ distvei3 + disthus + region + skogkategori + kant + helling + hohkatb + treartgruppe)

f2 <- formula(beitetrykkr ~ distvei3 + disthus + landsdel + skogkategori + kant + helling + hohkatb + treartgruppe)

H1a <- hurdle(f1, dist = "poisson",  
              data = browse_91)  

H1b <- hurdle(f1, dist = "negbin", 
              data = browse_91)  

H2b <- hurdle(f2, dist = "negbin", 
              data = browse_91)

H1c <- hurdle(f1, dist = "negbin", 
              data = browse91_dist) 

## These are glms that can be used instead of hurdle, so its possible to use effect plots. But it only works for poisson....
# H1btest <- glm(factor(beitetrykkr > 0) ~ distvei3 + disthus + region + skogkategori + kant + helling + hohkatb + treartgruppe, data = browse_91,
#                family = binomial(link = "cloglog"))
# dv0c <- glm(visits ~ gender + health + income + poly(age, 2), data = DoctorVisits, family = ztpoisson, subset = visits > 0)


hurdletest(H1b)
plot(residuals(H1b) ~ fitted(H1b))

summary(H1a)
summary(H1b)
summary(H1btest)
summary(H1c)

AIC(H1a, H1b, H2b, m5glm, m4lm, H1btest)
AIC(H1b, H1c)

plot(allEffects(H1btest))

```

##### Two-way model "old school" with first running a binomial glm with a binomial respose (browsing yes/no), then running a poisson glm 
```{r}

B1 <- glm(bt.binom ~ distvei1 + disthus + landsdel + skogkategori + treartgruppe + kant + helling + hohkatb, data = browse9,
            family = "binomial")
P1 <- glm(beitetrykk ~ distvei1 + disthus + landsdel + skogkategori + treartgruppe + kant + helling + hohkatb, data = browse9pos,
            family = "poisson") 
P2 <- glm(beitetrykk ~ distvei1 + landsdel + skogkategori + treartgruppe + kant + helling + hohkatb, data = browse9pos,
            family = "poisson") # Here I took out the distance to house, because it was not significant. However, when comparing both AIC, the models barely differ.



summary(B1)
summary(P1)
summary(P2)
plot(P1)
plot(P2)
AIC(P1, P2)

```




```{r}
mod1 <- glm(beitetrykk ~ distvei1 + disthus + landsdel + skogkategori + kant + helling + hohkatb + treartgruppe, family = "poisson", data = browse9)

mu <- predict(mod1, type = "response") # predict expected mean count
exp <- sum(dpois(x = 0, lambda = mu)) # sum the probabilities of a 0 count for each mean
exp # predicted number of 0's
sum(browse9$beitetrykk < 1, na.rm = TRUE)  # observed number of 0's

```

```{r}

cor((as.matrix(browse9[browse9$beitetrykk,c("distvei1", "disthus", "helling")])),
      use = "complete")
```

























