---
title: "05_browsing_pressure_new"
author: "anne"
date: "1 februar 2019"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



########################################################################
## Generell test for zero inflation for browsing response variable ##
#######################################################################
```{r}
load("processdata/browse.rda")

library(ggplot2)
library(ggpubr)

ggplot(browse, aes(beitetrykk9)) +
  geom_histogram(fill = "#0073C2FF") +
  theme_pubclean()

ggplot(browse, aes(bt100)) +
  geom_histogram(fill = "#0073C2FF") +
  theme_pubclean()

str(browse$beitetrykk9)
summary(browse$beitetrykk9)



#### Test for zero-inflation

# Use glmmTMB package to run glm
library("glmmTMB")
m_test_zi <- glm(beitetrykk9 ~ disthus + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac, family = poisson, data = browse)

library("performance")
check_zeroinflation(m_test_zi)

# # Check for zero-inflation
# 
#    Observed zeros: 5681
#   Predicted zeros: 1
#             Ratio: 0.00
# 
# Model is underfitting zeros (probable zero-inflation).



```





###################################################################################
##     HOUSE                HOUSE                 HOUSE                       #####
###################################################################################

##       House binary - First part of hurdle model to account for zero inflation  ##


## Bin house threshold distance to house

#### Load data house models
```{r}
load("processdata/browse.rda")
names(browse)

browse_house <- browse

names(browse_house)

```


#### Scale variables if necessary
```{r}

browse_house$disthus <- scale(browse_house$disthus)
browse_house$distvei2 <- scale(browse_house$distvei2)

browse_house$tretetthet9 <- scale(browse_house$tretetthet9)
browse_house$helling <- scale(browse_house$helling)
browse_house$HOH <- scale(browse_house$HOH)
browse_house$moose_density <- scale(browse_house$moose_density)

browse_house$disthus_600 <- scale(browse_house$disthus_600)
browse_house$disthus_500 <- scale(browse_house$disthus_500)
browse_house$disthus_400 <- scale(browse_house$disthus_400)
browse_house$disthus_350 <- scale(browse_house$disthus_350)
browse_house$disthus_300 <- scale(browse_house$disthus_300)

browse_house$disthus_200 <- scale(browse_house$disthus_200)

browse_house$disthus_150 <- scale(browse_house$disthus_150)

summary(browse_house$disthus_200)
```


#### Checking for the cut for disthus
```{r}
library(lme4)


bin_cuthouse1 <- glmer(factor(beitetrykk9 > 0) ~ disthus + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

bin_cuthouse2 <- glmer(factor(beitetrykk9 > 0) ~ disthus_600 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

bin_cuthouse3 <- glmer(factor(beitetrykk9 > 0) ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house) # BEST

bin_cuthouse4 <- glmer(factor(beitetrykk9 > 0) ~ disthus_400 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

bin_cuthouse5 <- glmer(factor(beitetrykk9 > 0) ~ disthus_350 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

bin_cuthouse6 <- glmer(factor(beitetrykk9 > 0) ~ disthus_300 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

bin_cuthouse7 <- glmer(factor(beitetrykk9 > 0) ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house) # BEST

bin_cuthouse8 <- glmer(factor(beitetrykk9 > 0) ~ disthus_150 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

```

#### AIC selection threshold house
```{r}
library(AICcmodavg)

candmods_bin_cuthouse <- list(bin_cuthouse1, bin_cuthouse2, bin_cuthouse3, bin_cuthouse4, bin_cuthouse5, bin_cuthouse6, bin_cuthouse7, bin_cuthouse8)
aictab(candmods_bin_cuthouse, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K     AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod7 19 21514.35       0.00   0.69   0.69 -10738.16
# Mod8 19 21516.61       2.26   0.22   0.91 -10739.29
# Mod6 19 21518.53       4.17   0.09   1.00 -10740.25
# Mod5 19 21526.92      12.57   0.00   1.00 -10744.44
# Mod4 19 21533.96      19.60   0.00   1.00 -10747.96
# Mod3 19 21545.22      30.87   0.00   1.00 -10753.59
# Mod2 19 21556.32      41.97   0.00   1.00 -10759.14
# Mod1 19 21589.06      74.70   0.00   1.00 -10775.51

```

#### Save browse_house dataset
```{r}
names(browse_house)
# browse_house <- browse_house[, -c(19:23)]
names(browse_house)
save(browse_house, file = "browse_house.rda")

browse_house$beite_bin <- ifelse(browse_house$beitetrykk9 == 0, 0, 1)

```


## Bin house models
```{r}
library(lme4)
browse_h_bin1 <- glmer(beite_bin ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)
summary(browse_h_bin1)

browse_h_bin2 <- glmer(beite_bin ~ disthus_200 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house) # BEST

browse_h_bin3 <- glmer(beite_bin ~ disthus_200 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

browse_h_bin4 <- glmer(beite_bin ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

browse_h_bin6 <- glmer(beite_bin ~ disthus_200 + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house)

## For these models to run, do not scale disthus
browse_h_bin5 <- glmer(beite_bin ~ log(disthus_200+1) + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = browse_house) 





```

#### AIC selection bin models
```{r}
library(AICcmodavg)

candmods_browse_house_bin <- list(browse_h_bin1, browse_h_bin2, browse_h_bin3, browse_h_bin4, browse_h_bin5, browse_h_bin6)
candmods_browse_house_bin <- list(browse_h_bin2, browse_h_bin5)
candmods_browse_house_bin <- list(browse_h_bin2, browse_h_bin6)
aictab(candmods_browse_house_bin, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K     AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod2 18 21512.64       0.00   0.58   0.58 -10738.31
# Mod1 19 21514.35       1.71   0.25   0.83 -10738.16
# Mod5 18 21515.14       2.50   0.17   1.00 -10739.56
# Mod6 14 21522.73      10.09   0.00   1.00 -10747.36
# Mod3 16 21549.96      37.32   0.00   1.00 -10758.97
# Mod4 17 21550.08      37.44   0.00   1.00 -10758.03

#       K     AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod1 18 21512.64        0.0   0.78   0.78 -10738.31
# Mod2 18 21515.14        2.5   0.22   1.00 -10739.56

#       K     AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod1 18 21512.64       0.00   0.99   0.99 -10738.31
# Mod2 14 21522.73      10.09   0.01   1.00 -10747.36

```

#### Summary bin house
```{r}
summary(browse_h_bin2)
# vcov(browse_h_bin5)
```



#### Plots bin house
```{r}
# library(effects)
# 
# plot(allEffects(rbrowse_h_bin)5)
# plot(effect("skogkategori", browse_h_bin5))


library(sjPlot)
plot_model(browse_h_bin2, type = "diag")
plot_model(browse_h_bin2, type = "eff")
plot_model(browse_h_bin2, type = "est")

library(performance)
# check_model(browse_h_bin2)
model_performance(browse_h_bin2)

 
# tab_model(rec_h_bin5, transform = NULL, 
#           show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, show.se = TRUE, show.std = NULL, show.p = TRUE, show.stat = FALSE, show.df = FALSE, show.zeroinf = FALSE, show.r2 = TRUE, show.icc = TRUE, show.adj.icc = FALSE, show.re.var = TRUE, show.aic = TRUE, show.dev = FALSE, show.obs = TRUE, p.threshold = c(0.05, 0.01, 0.001))

ggstatsplot::ggcoefstats(
  x = browse_h_bin2,
  title = "generalized linear mixed-effects model"
)

```

#### Save bin house
```{r}
save(browse_h_bin2, file = "browse_h_bin2.rda")

```






##       House beta - Second part of the hurdle, Beta  ##


## Load data house models
```{r}

## !! Use browse_house - all variables needed are in there !! ##
load("processdata/browse_house.rda")

# load("processdata/recruits.rda")
# recruits_house <- recruits

names(browse_house)
```


#### Prepare data set for second part of the hurdle
```{r}
browse_house <- browse_house[browse_house$bt100 > 0, ]
str(browse_house)
summary(browse_house$bt100)

```


#### Scale variables if necessary
```{r}
browse_house$disthus <- scale(browse_house$disthus)
browse_house$distvei2 <- scale(browse_house$distvei2)

browse_house$tretetthet9 <- scale(browse_house$tretetthet9)
browse_house$helling <- scale(browse_house$helling)
browse_house$HOH <- scale(browse_house$HOH)
browse_house$moose_density <- scale(browse_house$moose_density)

browse_house$disthus_600 <- scale(browse_house$disthus_600)
browse_house$disthus_500 <- scale(browse_house$disthus_500)
browse_house$disthus_400 <- scale(browse_house$disthus_400)
browse_house$disthus_350 <- scale(browse_house$disthus_350)
browse_house$disthus_300 <- scale(browse_house$disthus_300)
browse_house$disthus_200 <- scale(browse_house$disthus_200)
browse_house$disthus_150 <- scale(browse_house$disthus_150)

summary(browse_house$disthus_600)
```

#### Checking for the cut for disthus
```{r}
library(glmmTMB)

beta_cuthouse1 <- glmmTMB(bt100 ~ disthus + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())

beta_cuthouse2 <- glmmTMB(bt100 ~ disthus_600 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())

beta_cuthouse3 <- glmmTMB(bt100 ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())

beta_cuthouse4 <- glmmTMB(bt100 ~ disthus_400 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())

beta_cuthouse5 <- glmmTMB(bt100 ~ disthus_300 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())

beta_cuthouse6 <- glmmTMB(bt100 ~ disthus_350 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())

beta_cuthouse7 <- glmmTMB(bt100 ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family()) # BEST

beta_cuthouse8 <- glmmTMB(bt100 ~ disthus_150 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())

```

#### AIC selection threshold house
```{r}
library(AICcmodavg)

candmods_beta_cuthouse <- list(beta_cuthouse1, beta_cuthouse2, beta_cuthouse3, beta_cuthouse4, beta_cuthouse5, beta_cuthouse6, beta_cuthouse7, beta_cuthouse8)
candmods_beta_cuthouse <- list(beta_cuthouse1, beta_cuthouse2, beta_cuthouse3)
aictab(candmods_beta_cuthouse, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K     AICc Delta_AICc AICcWt Cum.Wt      LL
# Mod7 20 -9735.44       0.00   0.92   0.92 4887.75
# Mod8 20 -9729.12       6.32   0.04   0.95 4884.59
# Mod5 20 -9729.12       6.33   0.04   0.99 4884.58
# Mod6 20 -9724.88      10.57   0.00   1.00 4882.46
# Mod4 20 -9722.41      13.03   0.00   1.00 4881.23
# Mod3 20 -9719.25      16.19   0.00   1.00 4879.65
# Mod2 20 -9714.73      20.72   0.00   1.00 4877.39
# Mod1 20 -9702.34      33.10   0.00   1.00 4871.20

```


#### Save browse_house dataset
```{r}
## !! Use browse_house - all variables needed are in there !! ##


# names(browse_house)
# browse_house <- browse_house[, -c(4,18:23)]
# str(browse_house)
# save(browse_house, file = "browse_house.rda")

```







## Beta house models

Prepare data set for second part of the hurdle
```{r}
browse_house <- browse_house[browse_house$bt100 > 0, ]
str(browse_house)
summary(browse_house$bt100)

```

```{r}
library(glmmTMB)

browse_h_beta1 <- glmmTMB(bt100 ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())
summary(browse_h_beta1)

browse_h_beta2 <- glmmTMB(bt100 ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + tretetthet9 + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
            data = browse_house,
            family = beta_family())



```


#### AIC selection beta models
```{r}
library(AICcmodavg)

candmods_browse_house_beta <- list(browse_h_beta1,browse_h_beta2)
aictab(candmods_browse_house_beta, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K     AICc Delta_AICc AICcWt Cum.Wt      LL
# Mod2 19 -9736.17       0.00   0.59   0.59 4887.11
# Mod1 20 -9735.44       0.72   0.41   1.00 4887.75

```


#### Summary beta house
```{r}
summary(browse_h_beta2)
# vcov(rec_h_bin5)
```



#### Plots beta house
```{r}
# library(effects)
# plot(allEffects(rec_h_beta7))
# plot(effect("skogkategori", rec_h_beta7))

library(sjPlot)
plot_model(browse_h_beta2, type = "diag")
plot_model(browse_h_beta2, type = "eff")
plot_model(browse_h_beta2, type = "est")

library(performance)
# check_model(browse_h_beta2)
model_performance(browse_h_beta2)

# tab_model(rec_h_beta7, transform = NULL,
#           show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, show.se = TRUE, show.std = NULL, show.p = TRUE, show.stat = FALSE, show.df = FALSE, show.zeroinf = FALSE, show.r2 = TRUE, show.icc = TRUE, show.adj.icc = FALSE, show.re.var = TRUE, show.aic = TRUE, show.dev = FALSE, show.obs = TRUE, p.threshold = c(0.05, 0.01, 0.001)) 
# Is it not working because of the scaled variables?





ggstatsplot::ggcoefstats(
  x = browse_h_beta2,
  title = "generalized linear mixed-effects model"
) # Not sure what exactly this shows.

```


#### Save house beta model
```{r}
save(browse_h_beta2, file = "browse_h_beta2.rda")
```