---
title: "05_browsing_pressure_new"
author: "anne"
date: "1 februar 2019"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load data
```{r}

# load("processdata/browse9.2.rda")
load("processdata/browse9.2_dist.rda")
load("processdata/browse9.2pos_dist.rda")
```




#### Modelling spatial autocorrelation (https://onlinelibrary.wiley.com/doi/full/10.1111/j.2007.0906-7590.05171.x)
Change the projection and make coordinates and a spatial point data frame to make a shapefile

```{r}
library(tidyr)
unite(browse9.3, UTMmerge, c(UTM_OV_33, UTM_SN_33), remove = FALSE)
duplicated(browse9.3$UTMmerge)
```


```{r}

library(sp)
library(rgdal)

crs <- CRS("+proj=utm +zone=33 +ellps=GRS80 +units=m +no_defs")
coords <- cbind(browse9.3$UTM_OV_33, browse9.3$UTM_SN_33)
data_spdf <- SpatialPointsDataFrame(coords, browse9.3, proj4string = crs)
# plot(data_spdf)
writeOGR(data_spdf, dsn = "output", layer = "spac", driver = "ESRI Shapefile")

```


```{r}

library(spdep)
library(ape)

# spdep package:

# prepare neighbour lists for spatial autocorrelation analysis
# nb.list <- dnearneigh(as.matrix(browse9.3[browse9.3$beitetrykkr, c("UTM_OV_33", "UTM_SN_33")]), 0, 5000)
# nb.weights <- nb2listw(nb.list, zero.policy = TRUE)
# 
# moran.plot(resid_m1abin, nb.weights, zero.policy = TRUE, spChk = NULL, labels = TRUE, xlab = NULL, ylab = NULL, quiet = NULL)
# 
# resid_m1abin <- resid(m1abin, type = "pearson")
# resid_m1bbin <- resid(m1bbin, type = "pearson")
# 
# moran.test(browse9.3$beitetrykkr, nb.weights, zero.policy = TRUE, randomisation=TRUE,
#  alternative="greater", rank = FALSE, na.action=na.fail, spChk=NULL,
#  adjust.n=TRUE, drop.EI2=FALSE)
# 
# moran.test(resid_m1bbin, nb.weights, zero.policy = TRUE, randomisation=TRUE,
#  alternative="greater", rank = FALSE, na.action=na.fail, spChk=NULL,
#  adjust.n=TRUE, drop.EI2=FALSE)


# Make a matrix of coordinates - use when chunk above was not run
coords <- as.matrix(cbind(browse9.2$UTM_OV_33, browse9.2$UTM_SN_33))

# compute the autocovariate based on the above distance and weight
ac <- autocov_dist(browse9.2$beitetrykkr, coords, nbs = 5000, type="inverse", zero.policy = TRUE)
browse9.2$ac <- ac


save(browse9.2, file = "browse9.2.rda")


```




#### gam

```{r}
library(ggplot2)
ggplot(browse9.2, aes(x = disthus, y = beitetrykkr)) +
    geom_point() +
    stat_smooth(method = "glm", color = "green") +
  stat_smooth(color = "blue")

# +
#   scale_x_continuous(breaks=c(100,150, 200, 250, 300, 400, 500, 1000, 1500, 2000, 3000))

```

```{r}
library(mgcv)
gam1 <- gam(beitetrykkr ~ distvei2 + disthus + skogkategori + treartgruppe + region + kant + helling + HOH + tretetthet9,
             data = browse9.2,
             method = "REML")

gam2 <- gam(beitetrykkr ~ s(distvei2) + s(disthus) + skogkategori + treartgruppe + region + kant + helling + HOH + tretetthet9,
             data = browse9.2,
             method = "REML")

```

```{r}
plot.gam(gam1, all.terms = TRUE)
plot.gam(gam2, all.terms = TRUE)
# threshold: disthus ~700/900m, distvei2 ~200/300m
```





## Bin - First part of a hurdle model to account for zero inflation


##### Checking for the cut for disthus
```{r}
library(lme4)
m1abin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_scale + distvei2_trunc_scale + skogkategori + treartgruppe + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + ac_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2)

m1bbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut1000_scale + distvei2_trunc_scale + skogkategori + treartgruppe + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + ac_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2)

m1cbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut900_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2)

m1dbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut800_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2)

m1ebin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut700_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2) 

m1fbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut600_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2) 

m1gbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut500_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2) 

m1hbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut400_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2) 

m1ibin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut300_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2) 

m1jbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut200_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2) #10

m1kbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut150_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2) #11

m1lbin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_cut175_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2)

```

```{r}
library(AICcmodavg)

Candmods_bin <- list(m1abin, m1bbin, m1cbin, m1dbin, m1ebin, m1fbin, m1gbin, m1hbin, m1ibin, m1jbin, m1kbin, m1lbin)


glmmbin_tab <- aictab(Candmods_bin, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# cut175 is the thing!

```

##### Model selection bin
```{r}
library(lme4)

m2bin <- glmer(factor(beitetrykkr > 0) ~ log(disthus+1) + log(distvei2+1) + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + distvei2_trunc_scale*skogkategori + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m2abin <- glmer(factor(beitetrykkr > 0) ~ log(disthus+1) + log(distvei2+1) + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + log(distvei2+1)*skogkategori + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m3bin <- glmer(factor(beitetrykkr > 0) ~ log(disthus+1) + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + distvei2_trunc_scale*skogkategori + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m3abin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_scale + log(distvei2+1) + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + log(distvei2+1)*skogkategori + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m4bin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + distvei2_trunc_scale*skogkategori + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist) #1

m5bin <- glmer(factor(beitetrykkr > 0) ~ distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist) #2

m6bin <- glmer(factor(beitetrykkr > 0) ~ skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist) #3

m7bin <- glmer(factor(beitetrykkr > 0) ~ skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m8bin <- glmer(factor(beitetrykkr > 0) ~ treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m9bin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m10bin <- glmer(factor(beitetrykkr > 0) ~ distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m11bin <- glmer(factor(beitetrykkr > 0) ~ disthus_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m12bin <- glmer(factor(beitetrykkr > 0) ~ treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

```

```{r}
library(AICcmodavg)

Candmods_bin <- list(m4bin, m5bin, m6bin, m7bin, m8bin, m9bin, m10bin, m11bin, m12bin)

glmmbin_tab <- aictab(Candmods_bin, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# m4bin is the thing!
AIC(m2bin, m2abin, m3bin, m3abin, m4bin, m14bin)
# m2bin is the thing!

```

```{r}
m2bin <- glmer(factor(beitetrykkr > 0) ~ log(disthus+1) + log(distvei2+1) + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + distvei2_trunc_scale*skogkategori + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist) # OBS! same as m2bin in previous chunk

m13bin <- glmer(factor(beitetrykkr > 0) ~ log(disthus+1) + log(distvei2+1) + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + log(distvei2+1)*veitype2 + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m14bin <- glmer(factor(beitetrykkr > 0) ~ log(disthus+1) + log(distvei2+1) + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)
# warning: fixed-effect model matrix is rank deficient so dropping 1 column / coefficient, THEN it just drops the interaction

m15bin <- glmer(factor(beitetrykkr > 0) ~ log(distvei2+1) + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + distvei2_trunc_scale*skogkategori + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

m16bin <- glmer(factor(beitetrykkr > 0) ~ log(distvei2+1) + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            family = binomial(),
            data = browse9.2_dist)

```

```{r}
AIC(m2bin, m13bin, m14bin)
```


```{r}
# Check which optimizer doesn't converge
allFit(model)
```

Testing for normality of errors (Although I don't know if this works for binomial)
```{r}
summary(m4bin)

plot(m4bin)
hist(resid(m4bin))

resid.m4bin <- resid(m4bin)
plot(resid.m4bin)

par(mfrow = c(3,3))
plot(resid.m4bin ~ skogkategori, data = browse9.2_dist)
plot(resid.m4bin ~ treartgruppe, data = browse9.2_dist)
plot(resid.m4bin ~ kant, data = browse9.2_dist)
plot(resid.m4bin ~ helling_scale, data = browse9.2_dist)
plot(resid.m4bin ~ HOH_scale, data = browse9.2_dist)
plot(resid.m4bin ~ tretetthet9_trunc_scale, data = browse9.2_dist)
plot(resid.m4bin ~ disthus_trunc_scale, data = browse9.2_dist)
plot(resid.m4bin ~ distvei2_trunc_scale, data = browse9.2_dist)

library(sjPlot)
plot_model(m4bin, type = c("diag"), transform, terms = NULL)
# plot_model(m10bin, type = c("resid"), transform, terms = NULL)


```

Table of estimates:
```{r}
library(sjPlot)
tab_model(m4bin, transform = NULL, 
          show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, show.se = TRUE,
          show.std = NULL, show.p = TRUE, 
          show.stat = FALSE, show.df = FALSE, show.r2 = TRUE, 
          show.icc = TRUE, show.adj.icc = FALSE, show.re.var = TRUE, show.aic = TRUE, 
          show.dev = FALSE, show.obs = TRUE)


```

Forest plot:
Whiskers are ci, possible to show se instead; Colourblind friendly colours "#004949","#009292"
```{r}
p1 <- plot_model(m4bin, type = c("est"), transform = NULL, show.values = TRUE, value.offset = 0.5, 
                 vline.color = "grey", colors = c("#004949", "#009292"),
                 axis.title = "Estimates")
p1 + theme_sjplot() + font_size(axis_title.x = 15)

```

```{r}

p1 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("treartgruppe"),
           grid = TRUE)
# p3 + theme_sjplot()

p2 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("kant"))
# p4 + theme_sjplot()

p3 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("helling_scale [all]"))
# p5 + theme_sjplot()

p4 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("HOH_scale [all]"))
# p6 + theme_sjplot()

p5 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("tretetthet9_trunc_scale [all]"))
# p7 + theme_sjplot()

p6 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("distvei2_trunc_scale [all]"))
# p7 + theme_sjplot()

# p7 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("skogkategori"))
# # p7 + theme_sjplot()

p8 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("disthus_trunc_scale"))
# p7 + theme_sjplot()

p9 <- plot_model(m4bin, type = c("eff"), transform = NULL, terms = c("distvei2_trunc_scale [all]", "skogkategori"))
# p7 + theme_sjplot()


library(gridExtra)
plot_grid(list(p1, p2, p3, p4, p5, p6, p8, p9))


# library(effects)
# plot(allEffects(m4glmm))
```




## Beta - Second part of a hurdle model

##### Checking for the cut for disthus
```{r}
library(glmmTMB)
browse9.2pos <- browse9.2[browse9.2$bt100 > 0, ]

m1beta <- glmmTMB(bt100 ~ disthus_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1bbeta <- glmmTMB(bt100 ~ disthus_cut1000_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1cbeta <- glmmTMB(bt100 ~ disthus_cut900_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1dbeta <- glmmTMB(bt100 ~ disthus_cut800_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1ebeta <- glmmTMB(bt100 ~ disthus_cut700_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1fbeta <- glmmTMB(bt100 ~ disthus_cut600_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1gbeta <- glmmTMB(bt100 ~ disthus_cut500_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family()) #7

m1hbeta <- glmmTMB(bt100 ~ disthus_cut400_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family()) #8

m1ibeta <- glmmTMB(bt100 ~ disthus_cut200_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1jbeta <- glmmTMB(bt100 ~ disthus_cut175_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1kbeta <- glmmTMB(bt100 ~ disthus_cut150_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

m1lbeta <- glmmTMB(bt100 ~ disthus_cut190_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos,
            family = beta_family())

```


```{r}
AIC(m1beta, m1bbeta, m1cbeta, m1dbeta, m1ebeta, m1fbeta, m1gbeta, m1hbeta, m1ibeta, m1jbeta, m1kbeta, m1lbeta)

# cut200 is the thing!

```

##### Model selection beta
```{r}
library(glmmTMB)
browse9.2pos_dist <- browse9.2_dist[browse9.2_dist$bt100 > 0, ]

m2beta <- glmmTMB(bt100 ~ disthus_trunc_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos_dist,
            family = beta_family())

m3beta <- glmmTMB(bt100 ~ disthus_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos_dist,
            family = beta_family())

m4beta <- glmmTMB(bt100 ~ distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos_dist,
            family = beta_family())

m5beta <- glmmTMB(bt100 ~ skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + skogkategori*distvei2_trunc_scale + (1|KOMNR),
            data = browse9.2pos_dist,
            family = beta_family())

m6beta <- glmmTMB(bt100 ~ skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            data = browse9.2pos_dist,
            family = beta_family())

m7beta <- glmmTMB(bt100 ~ disthus_trunc_scale + distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            data = browse9.2pos_dist,
            family = beta_family())

m8beta <- glmmTMB(bt100 ~ distvei2_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            data = browse9.2pos_dist,
            family = beta_family())

m9beta <- glmmTMB(bt100 ~ disthus_trunc_scale + skogkategori + treartgruppe + ac_scale + kant + helling_scale + HOH_scale + I(HOH_scale^2) + tretetthet9_trunc_scale + (1|KOMNR),
            data = browse9.2pos_dist,
            family = beta_family())

```

```{r}
AIC(m2beta, m3beta, m4beta, m5beta, m6beta, m7beta, m8beta, m9beta)
# m7beta is the thing!
```



```{r}
resid_m7beta <- resid(m7beta, type = "pearson")
plot(resid_m7beta)

overdisp_fun <- function(model) {
    rdf <- df.residual(model)
    rp <- residuals(model,type="pearson")
    Pearson.chisq <- sum(rp^2)
    prat <- Pearson.chisq/rdf
    pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
    c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}

overdisp_fun(m7beta)
# Have overdispersion, but he (Ben Bolker) says: "Remember that (1) overdispersion is irrelevant for models that estimate a scale parameter (i.e. almost anything but Poisson or binomial: Gaussian, Gamma, negative binomial …) and (2) overdispersion is not estimable (and hence practically irrelevant) for Bernoulli models (= binary data = binomial with N=1)."
```

Table of estimates:
```{r}
library(sjPlot)

tab_model(m7beta, transform = NULL, 
          show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, show.se = TRUE, show.std = NULL, show.p = TRUE, show.stat = FALSE, show.df = FALSE, show.zeroinf = FALSE, show.r2 = TRUE, show.icc = TRUE, show.adj.icc = FALSE, show.re.var = TRUE, show.aic = TRUE, show.dev = FALSE, show.obs = TRUE, p.threshold = c(0.05, 0.01, 0.001))


```

Forest plot:
Whiskers are ci, possible to show se instead; Colourblind friendly colours "#004949","#009292"
```{r}
p1_est <- plot_model(m7beta, type = c("est"), transform = NULL, show.values = TRUE, value.offset = 0.5, 
                 vline.color = "grey", colors = c("#004949", "#009292"),
                 axis.title = "Estimates")
p1_est + theme_sjplot() + font_size(axis_title.x = 15)

```



```{r}
pb1 <- plot_model(m7beta, type = c("eff"), transform = NULL, terms = c("disthus_trunc_scale [all]"))
# pb1 + theme_sjplot()

pb2 <- plot_model(m7beta, type = c("eff"), transform = NULL, terms = c("distvei2_trunc_scale [all]"))
# pb1 + theme_sjplot()

pb3 <- plot_model(m7beta, type = c("eff"), transform = NULL, terms = c("skogkategori"))
# pb2 + theme_sjplot()

pb4 <- plot_model(m7beta, type = c("eff"), transform = NULL, terms = c("treartgruppe"),
                  show.p = TRUE)
# pb3 + theme_sjplot()

pb5 <- plot_model(m7beta, type = c("eff"), transform = NULL, terms = c("kant"))
# pb4 + theme_sjplot()

pb6 <- plot_model(m7beta, type = c("eff"), transform = NULL, terms = c("helling_scale [all]"))
# pb5 + theme_sjplot()

pb7 <- plot_model(m7beta, type = c("eff"), transform = NULL, terms = c("HOH_scale [all]"))
# pb6 + theme_sjplot()

pb8 <- plot_model(m7beta, type = c("eff"), transform = NULL, terms = c("tretetthet9_trunc_scale [all]"))
# pb7 + theme_sjplot()

plot_grid(list(pb1, pb2, pb3, pb4, pb5, pb6, pb7, pb8))


# type = "pred" = Predicted values (marginal effects) for specific model terms. See ggpredict for details.
# type = "eff" = Similar to type = "pred", however, discrete predictors are held constant at their proportions (not reference level). See ggeffect for details. ggeffect() computes marginal effects by internally calling Effect. Effect constructs an "eff" object for a term (usually a high-order term), absorbing the lower-order terms marginal to the term in question, and averaging over other terms in the model.

```