---
title: "09_recruitment_hurdle_remake"
author: "Anne"
date: "12/04/2021"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


########################################################################
## Generell test for zero inflation for recruitment response variable ##
#######################################################################
```{r}
load("processdata/recruits_2021_02_01.rda")

library(ggplot2)
library(ggpubr)

ggplot(recruits, aes(recruitment)) +
  geom_histogram(fill = "#0073C2FF") +
  theme_pubclean()

str(recruits$recruitment)
summary(recruits$recruitment)



#### Test for zero-inflation

# Use glmmTMB package to run glm
library("glmmTMB")
m_test_zi <- glm(recruitment ~ disthus + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac, family = poisson, data = recruits)

library("performance")
check_zeroinflation(m_test_zi)

# # Check for zero-inflation
# 
#    Observed zeros: 13066
#   Predicted zeros: 4
#             Ratio: 0.00
# 
# Model is underfitting zeros (probable zero-inflation).



```


##       BINARY - First part of hurdle model to account for zero inflation  ##


## Bin threshold distance to house

#### Load data house threshold
```{r}
load("processdata/recruits_2021_02_01.rda")
names(recruits)

recruits_house <- recruits

# load("processdata/recruits_house.rda")

names(recruits_house)
```


#### Scale variables if necessary
```{r}

recruits_house$disthus <- scale(recruits_house$disthus)

recruits_house$distvei2 <- scale(recruits_house$distvei2)

# recruits_house$beitetrykk9 <- scale(recruits_house$beitetrykk9)
recruits_house$helling <- scale(recruits_house$helling)
recruits_house$HOH <- scale(recruits_house$HOH)
recruits_house$moose_density <- scale(recruits_house$moose_density)

recruits_house$disthus_600 <- scale(recruits_house$disthus_600)

recruits_house$disthus_500 <- scale(recruits_house$disthus_500)

recruits_house$disthus_400 <- scale(recruits_house$disthus_400)
recruits_house$disthus_350 <- scale(recruits_house$disthus_350)
recruits_house$disthus_300 <- scale(recruits_house$disthus_300)
recruits_house$disthus_200 <- scale(recruits_house$disthus_200)
recruits_house$disthus_150 <- scale(recruits_house$disthus_150)

summary(recruits_house$disthus)
```


#### Checking for the cut for disthus
```{r}
library(lme4)

bin_cuthouse1 <- glmer(factor(recruitment > 0) ~ disthus + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse2 <- glmer(factor(recruitment > 0) ~ disthus_600 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse3 <- glmer(factor(recruitment > 0) ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house) # BEST

bin_cuthouse4 <- glmer(factor(recruitment > 0) ~ disthus_400 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse5 <- glmer(factor(recruitment > 0) ~ disthus_350 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse6 <- glmer(factor(recruitment > 0) ~ disthus_300 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse7 <- glmer(factor(recruitment > 0) ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse8 <- glmer(factor(recruitment > 0) ~ disthus_150 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

```

#### AIC selection threshold house
```{r}
library(AICcmodavg)

candmods_bin_cuthouse <- list(bin_cuthouse1, bin_cuthouse2, bin_cuthouse3, bin_cuthouse4, bin_cuthouse5, bin_cuthouse6, bin_cuthouse7, bin_cuthouse8)
aictab(candmods_bin_cuthouse, modnames = NULL,
                       second.ord = F, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K      AIC Delta_AIC AICWt Cum.Wt        LL
# 500  19 22815.51      0.00  0.47   0.47 -11388.76
# 600  19 22815.58      0.07  0.46   0.93 -11388.79
# 400  19 22819.32      3.81  0.07   1.00 -11390.66
# 350  19 22825.61     10.10  0.00   1.00 -11393.81
# 300  19 22833.41     17.90  0.00   1.00 -11397.71
# 200  19 22847.68     32.17  0.00   1.00 -11404.84
# 150  19 22861.53     46.02  0.00   1.00 -11411.76
# full 19 22886.53     71.02  0.00   1.00 -11424.27

```

#### Save recruits_house dataset
```{r}
str(recruits)
names(recruits)
recruits_house <- recruits[, -c(4,19:23)]
names(recruits_house)
save(recruits_house, file = "recruits_house_2021_02_02.rda")

```




## Bin house models

#### Load data
```{r}
load("processdata/recruits_house_2021_02_02.rda")
str(recruits_house)
recruits_house$recruitment_bin <- ifelse(recruits_house$recruitment == 0, 0, 1)

```

#### Scale variables if necessary
```{r}

# recruits_house$disthus <- scale(recruits_house$disthus)

# recruits_house$distvei2 <- scale(recruits_house$distvei2)

# recruits_house$beitetrykk9 <- scale(recruits_house$beitetrykk9)
recruits_house$helling <- scale(recruits_house$helling)
recruits_house$HOH <- scale(recruits_house$HOH)
# recruits_house$moose_density <- scale(recruits_house$moose_density)
recruits_house$tretetthet9 <- scale(recruits_house$tretetthet9)

# recruits_house$disthus_600 <- scale(recruits_house$disthus_600)
recruits_house$disthus_500 <- scale(recruits_house$disthus_500)

summary(recruits_house$helling)
```



```{r}
library(lme4)
rec_h_bin1 <- glmer(recruitment_bin ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density + tretetthet9 +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

rec_h_bin2 <- glmer(recruitment_bin ~ log(disthus+1) + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

rec_h_bin3 <- glmer(recruitment_bin ~ disthus_500 + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density + tretetthet9 +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)  # BEST
summary(rec_h_bin3)




```

#### AIC selection bin models
```{r}
library(AICcmodavg)

candmods_rec_house_bin <- list(rec_h_bin1, rec_h_bin2, rec_h_bin3)
aictab(candmods_rec_house_bin, modnames = NULL,
                       second.ord = F, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K      AIC Delta_AIC AICWt Cum.Wt        LL
# Mod3 20 21536.66      0.00     1      1 -10748.33
# Mod1 20 21557.53     20.87     0      1 -10758.77
# Mod2 19 22793.06   1256.39     0      1 -11377.53

```

#### Summary bin house
```{r}
summary(rec_h_bin3)
```



#### Plots bin house
```{r}
library(sjPlot)
plot_model(rec_h_bin3, type = "diag")
plot_model(rec_h_bin3, type = "eff")
plot_model(rec_h_bin3, type = "est")


 
tab_model(rec_h_bin3, transform = NULL,
          show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, p.threshold = c(0.05, 0.01, 0.001))


```

#### Save bin house
```{r}
save(rec_h_bin3, file = "output/recruitment_2021_04_12/rec_h_bin3.rda")

```






##       ZERO-TRUNCATED - Second part of the hurdle, Poisson  ##


## Load data house threshold
```{r}

load("processdata/recruits_2021_02_01.rda")
names(recruits)

recruits_house <- recruits

str(recruits_house)

```



#### Prepare data set for second part of the hurdle
```{r}
recruits_house <- recruits_house[recruits_house$recruitment > 0, ]
str(recruits_house)
summary(recruits_house$recruitment)

is.integer(recruits_house$recruitment)
recruits_house$recruitment <- as.integer(recruits_house$recruitment)
is.integer(recruits_house$recruitment)
```


#### Scale variables if necessary
```{r}
recruits_house$disthus <- scale(recruits_house$disthus)
recruits_house$distvei2 <- scale(recruits_house$distvei2)

# recruits_house$beitetrykk9 <- scale(recruits_house$beitetrykk9)
recruits_house$helling <- scale(recruits_house$helling)
recruits_house$HOH <- scale(recruits_house$HOH)
recruits_house$moose_density <- scale(recruits_house$moose_density)

recruits_house$disthus_600 <- scale(recruits_house$disthus_600)

recruits_house$disthus_500 <- scale(recruits_house$disthus_500)

recruits_house$disthus_400 <- scale(recruits_house$disthus_400)
recruits_house$disthus_350 <- scale(recruits_house$disthus_350)
recruits_house$disthus_300 <- scale(recruits_house$disthus_300)
recruits_house$disthus_200 <- scale(recruits_house$disthus_200)
recruits_house$disthus_150 <- scale(recruits_house$disthus_150)

summary(recruits_house$disthus_600)
```

#### Checking for the threshold for disthus
```{r}
library(lme4)


beta_cuthouse1 <- glmer(recruitment ~ disthus + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house)

beta_cuthouse2 <- glmer(recruitment ~ disthus_600 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house) # BEST

beta_cuthouse3 <- glmer(recruitment ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house) 

beta_cuthouse4 <- glmer(recruitment ~ disthus_400 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house)

beta_cuthouse5 <- glmer(recruitment ~ disthus_350 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house)

beta_cuthouse6 <- glmer(recruitment ~ disthus_300 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house)

beta_cuthouse7 <- glmer(recruitment ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house)

beta_cuthouse8 <- glmer(recruitment ~ disthus_150 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house)

```

#### AIC selection threshold house
```{r}
library(AICcmodavg)

candmods_beta_cuthouse <- list(beta_cuthouse1, beta_cuthouse2, beta_cuthouse3, beta_cuthouse4, beta_cuthouse5, beta_cuthouse6, beta_cuthouse7, beta_cuthouse8)
# candmods_beta_cuthouse <- list(beta_cuthouse1, beta_cuthouse2, beta_cuthouse3)
aictab(candmods_beta_cuthouse, modnames = NULL,
                       second.ord = F, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K     AIC Delta_AIC AICWt Cum.Wt        LL
# 600  19 1145906      0.00     1      1 -572933.9
# 500  19 1145926     20.57     0      1 -572944.2
# 400  19 1147153   1247.54     0      1 -573557.7
# 350  19 1147952   2045.83     0      1 -573956.8
# 300  19 1148915   3008.94     0      1 -574438.4
# 200  19 1150628   4722.33     0      1 -575295.1
# 150  19 1150812   4906.55     0      1 -575387.2
# full 19 1153297   7391.18     0      1 -576629.5

```



## Zero-truncated house data

#### Load models
```{r}
load("processdata/recruits_house.rda")
str(recruits_house)
names(recruits_house)
```


#### Prepare data set for second part of the hurdle
```{r}
recruits_house <- recruits_house[recruits_house$recruitment > 0, ]
str(recruits_house)
summary(recruits_house$recruitment)

is.integer(recruits_house$recruitment)
recruits_house$recruitment <- as.integer(recruits_house$recruitment)
is.integer(recruits_house$recruitment)
```


#### Scale variables if necessary
```{r}
# recruits_house$disthus <- scale(recruits_house$disthus)

# recruits_house$distvei2 <- scale(recruits_house$distvei2)

# recruits_house$beitetrykk9 <- scale(recruits_house$beitetrykk9)
recruits_house$helling <- scale(recruits_house$helling)
recruits_house$HOH <- scale(recruits_house$HOH)
# recruits_house$moose_density <- scale(recruits_house$moose_density)
recruits_house$tretetthet9 <- scale(recruits_house$tretetthet9)

recruits_house$disthus_600 <- scale(recruits_house$disthus_600)
recruits_house$disthus_500 <- scale(recruits_house$disthus_500)

# summary(recruits_house$disthus_600)
```


#### Zero-truncated house models
```{r}
library(lme4)
rec_h_beta1 <- glmer(recruitment ~ disthus_600 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density + tretetthet9 + ac + (1|KOMNR),
family = poisson(),
data = recruits_house)
summary(rec_h_beta1)

rec_h_beta2 <- glmer(recruitment ~ log(disthus+1) + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density + tretetthet9 + ac + (1|KOMNR),
family = poisson(),
data = recruits_house)

rec_h_beta3 <- glmer(recruitment ~ disthus_600 + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density + tretetthet9 + ac + (1|KOMNR),
family = poisson(),
data = recruits_house)
summary(rec_h_beta3)

rec_h_beta4 <- glmer(recruitment ~ disthus_600 + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + tretetthet9 + ac + (1|KOMNR),
family = poisson(),
data = recruits_house) # BEST

rec_h_beta5 <- glmer(recruitment ~ log(disthus_600+1) + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + tretetthet9 + ac + (1|KOMNR),
family = poisson(),
data = recruits_house)


library(glmmTMB)
rec_h_beta4_TMB <- glmmTMB(recruitment ~ disthus_600 + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + tretetthet9 + ac + (1|KOMNR),
                           family = poisson,
                           data = recruits_house) # Same as rec_h_beta4, just run with glmmTMB

rec_h_beta4_TMB_500 <- glmmTMB(recruitment ~ disthus_500 + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + tretetthet9 + ac + (1|KOMNR),
                           family = poisson,
                           data = recruits_house) # Same as rec_h_beta4_TMB, just run with disthus_500 to adjust to the other models

summary(rec_h_beta4_TMB_500)
save(rec_h_beta4_TMB_500, file = "output/recruitment_2021_04_12/rec_h_beta4_TMB_500.rda")



```


#### AIC selection beta models
```{r}
library(AICcmodavg)

candmods_rec_house_beta <- list(rec_h_beta1, rec_h_beta2, rec_h_beta3, rec_h_beta4, rec_h_beta5)
aictab(candmods_rec_house_beta, modnames = NULL,
                       second.ord = F, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K     AIC Delta_AIC AICWt Cum.Wt        LL
# Mod4 19 1016400      0.00  0.71   0.71 -508181.1
# Mod3 20 1016402      1.79  0.29   1.00 -508181.0
# Mod5 19 1017275    874.87  0.00   1.00 -508618.5
# Mod1 20 1017547   1146.48  0.00   1.00 -508753.3
# Mod2 20 1018674   2273.90  0.00   1.00 -509317.0



```


#### Summary beta house
```{r}
summary(rec_h_beta4_TMB)
summary(rec_h_beta4_TMB_500)
```



#### Plots beta house
```{r}
library(sjPlot)
plot_model(rec_h_beta4_TMB, type = "diag")
plot_model(rec_h_beta4_TMB, type = "eff")
plot_model(rec_h_beta4_TMB_500, type = "eff")
plot_model(rec_h_beta4_TMB, type = "est")

tab_model(rec_h_beta4_TMB_500, transform = NULL,
          show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, p.threshold = c(0.05, 0.01, 0.001))

```


#### Save house beta model
```{r}
save(rec_h_beta4_TMB_500, file = "output/recruitment_2021_04_12/rec_h_beta4_TMB_500.rda")
```






## Delta AIC comparison figure
```{r}
library(readr)
delta_aic_comparison <- read_csv("figs_tabs/delta_aic_comparison.csv", na = "NA")
str(delta_aic_comparison)

delta_aic_comparison <- delta_aic_comparison[-c(9), ]
str(delta_aic_comparison)

library(ggplot2)
overview <- ggplot() + 
  geom_point(data = delta_aic_comparison, aes(x = threshold, y = delta_aic_bp_bin, color = "Browsing pressure\nbinary\n"), show.legend = T) + 
  geom_point(data = delta_aic_comparison, aes(x = threshold, y = delta_aic_bp_zt, color = "Browsing pressure\nzero-truncated\n"), show.legend = T) + 
  geom_point(data = delta_aic_comparison, aes(x = threshold, y = delta_aic_rec_bin, color = "recruitment\nbinary\n"), show.legend = T) + 
  geom_point(data = delta_aic_comparison, aes(x = threshold, y = delta_aic_rec_zt, color = "recruitment\nzero-truncated"), show.legend = T) +
  labs(x="Threshold cut-off\n", y = "delta AIC\n")+
   theme_classic() +
  scale_color_manual(name = "Model", 
                     values = c("Browsing pressure\nbinary\n" = "#56B4E9", "Browsing pressure\nzero-truncated\n" = "#0072B2", "recruitment\nbinary\n" = "#b37c00", "recruitment\nzero-truncated" = "#E69F00")) +
  scale_x_continuous(breaks = c(0, 100, 200, 300, 400, 500, 600, 3000)) +
  scale_y_continuous(breaks = c(0, 500, 1000, 2000, 3000, 4000, 5000, 7500))




detail <- ggplot() + 
  geom_vline(xintercept = 500, linetype="solid", color = "grey70", size=1) + 
  geom_hline(yintercept = 20, linetype="solid", color = "grey70", size=1) + 
  geom_hline(yintercept = 10, linetype="dashed", color = "grey80", size=1) + 
  geom_point(data = delta_aic_comparison, aes(x = threshold, y = delta_aic_bp_bin, color = "Browsing pressure\nbinary\n"), show.legend = T) + 
  geom_point(data = delta_aic_comparison, aes(x = threshold, y = delta_aic_bp_zt, color = "Browsing pressure\nzero-truncated\n"), show.legend = T) + 
  geom_point(data = delta_aic_comparison, aes(x = threshold, y = delta_aic_rec_bin, color = "recruitment\nbinary\n"), show.legend = T) + 
  geom_point(data = delta_aic_comparison, aes(x = threshold, y = delta_aic_rec_zt, color = "recruitment\nzero-truncated"), show.legend = T) +
  labs(x="Threshold cut-off\n", y = "delta AIC\n")+
   theme_classic() +
  scale_color_manual(name = "Model", 
                     values = c("Browsing pressure\nbinary\n" = "#56B4E9", "Browsing pressure\nzero-truncated\n" = "#0072B2", "recruitment\nbinary\n" = "#b37c00", "recruitment\nzero-truncated" = "#E69F00")) +
  scale_x_continuous(breaks = c(0, 100, 200, 300, 400, 500, 600, 3000)) +
  scale_y_continuous(breaks = c(0, 5, 10, 20, 30, 40, 50))+ 
  coord_cartesian(xlim = c(0, 600), ylim = c(0, 50))

```




