---
title: "recruitment"
author: "Anne"
date: "27/11/2020"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




########################################################################
## Generell test for zero inflation for recruitment response variable ##
#######################################################################
```{r}
load("processdata/recruits.rda")

library(ggplot2)
library(ggpubr)

ggplot(recruits, aes(recruitment)) +
  geom_histogram(fill = "#0073C2FF") +
  theme_pubclean()

str(recruits$recruitment)
summary(recruits$recruitment)


recruits_house$recruitment <- as.integer(recruits_house$recruitment)
str(recruits_house$recruitment)

#### Test for zero-inflation

# Use glmmTMB package to run glm
library("glmmTMB")
m_test_zi <- glm(recruitment ~ disthus + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac, family = poisson, data = recruits_house)

library("performance")
check_zeroinflation(m_test_zi)

# Check for zero-inflation

#    Observed zeros: 13384
#   Predicted zeros: 4
#             Ratio: 0.00
# 
# Model is underfitting zeros (probable zero-inflation).



```




###################################################################################
##     HOUSE                HOUSE                 HOUSE                       #####
###################################################################################

##       House binary - First part of hurdle model to account for zero inflation  ##


## Bin house threshold distance to house

#### Load data house models
```{r}
load("processdata/recruits.rda")
names(recruits)

recruits_house <- recruits

# load("processdata/recruits_house.rda")

names(recruits_house)
```
#### Scale variables if necessary
```{r}
recruits_house$recr_bin <- ifelse(recruits_house$recruitment == 0, 0, 1)

recruits_house$disthus <- scale(recruits_house$disthus)
recruits_house$distvei2 <- scale(recruits_house$distvei2)

recruits_house$beitetrykk9 <- scale(recruits_house$beitetrykk9)
recruits_house$helling <- scale(recruits_house$helling)
recruits_house$HOH <- scale(recruits_house$HOH)
recruits_house$moose_density <- scale(recruits_house$moose_density)
recruits_house$disthus_600 <- scale(recruits_house$disthus_600)

recruits_house$disthus_500 <- scale(recruits_house$disthus_500)

recruits_house$disthus_400 <- scale(recruits_house$disthus_400)
recruits_house$disthus_350 <- scale(recruits_house$disthus_350)
recruits_house$disthus_300 <- scale(recruits_house$disthus_300)
recruits_house$disthus_200 <- scale(recruits_house$disthus_200)
recruits_house$disthus_150 <- scale(recruits_house$disthus_150)

summary(recruits_house$disthus)
```


#### Checking for the cut for disthus
```{r}
library(lme4)

# fitting glmm with glmmTMB
# glmmTMB(count~spp + (1|site), Salamanders, family=poisson)


bin_cuthouse1 <- glmer(recr_bin ~ disthus + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse2 <- glmer(recr_bin ~ disthus_600 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse3 <- glmer(recr_bin ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house) # BEST

bin_cuthouse4 <- glmer(recr_bin ~ disthus_400 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse5 <- glmer(recr_bin ~ disthus_350 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse6 <- glmer(recr_bin ~ disthus_300 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse7 <- glmer(recr_bin ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

bin_cuthouse8 <- glmer(recr_bin ~ disthus_150 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

```

#### AIC selection threshold house
```{r}
library(AICcmodavg)

candmods_bin_cuthouse <- list(bin_cuthouse1, bin_cuthouse2, bin_cuthouse3, bin_cuthouse4, bin_cuthouse5, bin_cuthouse6, bin_cuthouse7, bin_cuthouse8)
aictab(candmods_bin_cuthouse, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)


```

#### Save recruits_house_bin dataset
```{r}
names(recruits_house)
recruits_house_bin <- recruits_house[, -c(8,12:13,17:22)]
names(recruits_house_bin)
save(recruits_house_bin, file = "recruits_house_bin.rda")

```




## Bin house models
```{r}
library(lme4)
rec_h_bin1 <- glmer(recr_bin ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)
summary(rec_h_bin1)

rec_h_bin2 <- glmer(recr_bin ~ disthus_500 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

rec_h_bin3 <- glmer(recr_bin ~ skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

rec_h_bin4 <- glmer(recr_bin ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house)

rec_h_bin5 <- glmer(recr_bin ~ log(disthus_500+1) + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house) 

rec_h_bin6 <- glmer(recr_bin ~ log(disthus_500+1) + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house) # Too high: Model failed to converge with max|grad| = 0.826257 (tol = 0.002, component 1)

rec_h_bin7 <- glmer(recr_bin ~ disthus_500 + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_house) # BEST

```

#### AIC selection bin models
```{r}
library(AICcmodavg)

candmods_rec_house_bin <- list(rec_h_bin1, rec_h_bin2, rec_h_bin3, rec_h_bin4, rec_h_bin5, rec_h_bin7)
candmods_rec_house_bin <- list(rec_h_bin5, rec_h_bin6, rec_h_bin7)
aictab(candmods_rec_house_bin, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)


#       K     AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod3 19 23196.99       0.00   0.58   0.58 -11579.48
# Mod1 19 23197.64       0.65   0.42   1.00 -11579.80
# Mod2 19 23240.85      43.86   0.00   1.00 -11601.41
```
#### Summary bin house
```{r}
summary(rec_h_bin7)
# vcov(rec_h_bin5)
```



#### Plots bin house
```{r}
# library(effects)
# 
# plot(allEffects(rec_h_bin)5)
# plot(effect("skogkategori", rec_h_bin5))

library(sjPlot)
plot_model(rec_h_bin7, type = "diag")
plot_model(rec_h_bin7, type = "eff")
plot_model(rec_h_bin7, type = "est")
 
# tab_model(rec_h_bin5, transform = NULL, 
#           show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, show.se = TRUE, show.std = NULL, show.p = TRUE, show.stat = FALSE, show.df = FALSE, show.zeroinf = FALSE, show.r2 = TRUE, show.icc = TRUE, show.adj.icc = FALSE, show.re.var = TRUE, show.aic = TRUE, show.dev = FALSE, show.obs = TRUE, p.threshold = c(0.05, 0.01, 0.001))

ggstatsplot::ggcoefstats(
  x = rec_h_bin7,
  title = "generalized linear mixed-effects model"
)

```

#### Save bin house
```{r}
save(rec_h_bin7, file = "rec_h_bin7.rda")

```




##       House beta - Second part of the hurdle, Poisson  ##


## Load data house models
```{r}
load("processdata/recruits.rda")
recruits_house <- recruits

names(recruits_house)
```


#### Prepare data set for second part of the hurdle
```{r}
recruits_house_beta <- recruits[recruits_house$recruitment > 0, ]
str(recruits_house_beta)
summary(recruits_house_beta$recruitment)

is.integer(recruits_house_beta$recruitment)
recruits_house_beta$recruitment <- as.integer(recruits_house_beta$recruitment)
is.integer(recruits_house_beta$recruitment)
```


#### Scale variables if necessary
```{r}
recruits_house_beta$disthus <- scale(recruits_house_beta$disthus)
recruits_house_beta$distvei2 <- scale(recruits_house_beta$distvei2)

recruits_house_beta$beitetrykk9 <- scale(recruits_house_beta$beitetrykk9)
recruits_house_beta$helling <- scale(recruits_house_beta$helling)
recruits_house_beta$HOH <- scale(recruits_house_beta$HOH)
recruits_house_beta$moose_density <- scale(recruits_house_beta$moose_density)
recruits_house_beta$disthus_600 <- scale(recruits_house_beta$disthus_600)

recruits_house_beta$disthus_500 <- scale(recruits_house_beta$disthus_500)

recruits_house_beta$disthus_400 <- scale(recruits_house_beta$disthus_400)
recruits_house_beta$disthus_350 <- scale(recruits_house_beta$disthus_350)
recruits_house_beta$disthus_300 <- scale(recruits_house_beta$disthus_300)
recruits_house_beta$disthus_200 <- scale(recruits_house_beta$disthus_200)
recruits_house_beta$disthus_150 <- scale(recruits_house_beta$disthus_150)

summary(recruits_house_beta$disthus)
```

#### Checking for the cut for disthus
```{r}
library(lme4)


beta_cuthouse1 <- glmer(recruitment ~ disthus + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)
summary(beta_cuthouse1)


beta_cuthouse2 <- glmer(recruitment ~ disthus_600 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

beta_cuthouse3 <- glmer(recruitment ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta) # BEST

beta_cuthouse4 <- glmer(recruitment ~ disthus_400 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

beta_cuthouse5 <- glmer(recruitment ~ disthus_350 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

beta_cuthouse6 <- glmer(recruitment ~ disthus_300 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

beta_cuthouse7 <- glmer(recruitment ~ disthus_200 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

beta_cuthouse8 <- glmer(recruitment ~ disthus_150 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

```

#### AIC selection threshold house
```{r}
library(AICcmodavg)

candmods_beta_cuthouse <- list(beta_cuthouse1, beta_cuthouse2, beta_cuthouse3, beta_cuthouse4, beta_cuthouse5, beta_cuthouse6, beta_cuthouse7, beta_cuthouse8)
aictab(candmods_beta_cuthouse, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K    AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod3 19 1169628       0.00      1      1 -584795.1
# Mod2 19 1169652      24.02      0      1 -584807.1
# Mod4 19 1170944    1315.69      0      1 -585452.9
# Mod5 19 1171870    2241.21      0      1 -585915.7
# Mod6 19 1172960    3331.47      0      1 -586460.8
# Mod7 19 1174929    5300.67      0      1 -587445.4
# Mod8 19 1175241    5612.60      0      1 -587601.4
# Mod1 19 1177803    8174.82      0      1 -588882.5

```


#### Save recruits_house_beta dataset
```{r}
names(recruits_house_beta)
recruits_house_beta <- recruits_house_beta[, -c(4,13,17:22)]
save(recruits_house_beta, file = "recruits_house_beta.rda")

```


## Beta house models
```{r}
library(lme4)
rec_h_beta1 <- glmer(recruitment ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

summary(rec_h_beta1)

rec_h_beta2 <- glmer(recruitment ~ disthus_500 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

rec_h_beta3 <- glmer(recruitment ~ distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

rec_h_beta4 <- glmer(recruitment ~ disthus_500 + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta)

## For this to run, do not scale disthus_500 and distvei2 (because of the log())
rec_h_beta5 <- glmer(recruitment ~ log(disthus_500+1) + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta) 

rec_h_beta6 <- glmer(recruitment ~ log(disthus_500+1) + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta) # way too large: Model failed to converge with max|grad| = 1.31087

rec_h_beta7 <- glmer(recruitment ~ disthus_500 + log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
family = poisson(),
data = recruits_house_beta) # BEST


```


#### AIC selection beta models
```{r}
library(AICcmodavg)

candmods_rec_house_beta <- list(rec_h_beta1, rec_h_beta2, rec_h_beta3, rec_h_beta4)
candmods_rec_house_beta <- list(rec_h_beta4, rec_h_beta5, rec_h_beta6, rec_h_beta7)
aictab(candmods_rec_house_beta, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K    AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod4 18 1169627       0.00   0.66   0.66 -584795.4
# Mod1 19 1169628       1.31   0.34   1.00 -584795.1
# Mod2 18 1171848    2220.86   0.00   1.00 -585905.9
# Mod3 18 1178858    9231.21   0.00   1.00 -589411.1

#       K    AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod4 18 1167508       0.00      1      1 -583736.1
# Mod2 18 1168672    1163.47      0      1 -584317.8
# Mod1 18 1169627    2118.74      0      1 -584795.4
# Mod3 18 1170787    3278.26      0      1 -585375.2
```


#### Summary beta house
```{r}
summary(rec_h_beta7)
# vcov(rec_h_bin5)
```



#### Plots beta house
```{r}
# library(effects)
# plot(allEffects(rec_h_beta7))
# plot(effect("skogkategori", rec_h_beta7))

library(sjPlot)
plot_model(rec_h_beta7, type = "diag")
plot_model(rec_h_beta7, type = "eff")
plot_model(rec_h_beta7, type = "est")

# tab_model(rec_h_beta7, transform = NULL,
#           show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, show.se = TRUE, show.std = NULL, show.p = TRUE, show.stat = FALSE, show.df = FALSE, show.zeroinf = FALSE, show.r2 = TRUE, show.icc = TRUE, show.adj.icc = FALSE, show.re.var = TRUE, show.aic = TRUE, show.dev = FALSE, show.obs = TRUE, p.threshold = c(0.05, 0.01, 0.001)) 
# Is it not working because of the scaled variables?





ggstatsplot::ggcoefstats(
  x = rec_h_beta7,
  title = "generalized linear mixed-effects model"
) # Not sure what exactly this shows.

```


#### Save house beta model
```{r}
save(rec_h_beta7, file = "rec_h_beta7.rda")
```








###################################################################################
##     ROADS                ROADS                 ROADS                       #####
###################################################################################

##       Roads Bin - First part of a hurdle model to account for zero inflation  ##


## Bin house threshold distance to house

#### Load data house models
```{r}
load("processdata/recruits_roads.rda")
names(recruits_roads)

```



#### Scale variables if necessary
```{r}
recruits_roads$recr_bin <- ifelse(recruits_roads$recruitment == 0, 0, 1)

recruits_roads$disthus <- scale(recruits_roads$disthus)
# recruits_roads$distvei2 <- scale(recruits_roads$distvei2)
recruits_roads$beitetrykk9 <- scale(recruits_roads$beitetrykk9)
recruits_roads$helling <- scale(recruits_roads$helling)
recruits_roads$HOH <- scale(recruits_roads$HOH)
recruits_roads$moose_density <- scale(recruits_roads$moose_density)

summary(recruits_roads$disthus)
```



## Bin roads models
```{r}
library(lme4)
rec_r_bin1 <- glmer(recr_bin ~ disthus + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_roads)
summary(rec_r_bin1) 

rec_r_bin2 <- glmer(recr_bin ~ distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_roads) 

rec_r_bin3 <- glmer(recr_bin ~ disthus + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_roads)

rec_r_bin4 <- glmer(recr_bin ~ skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_roads)

rec_r_bin5 <- glmer(recr_bin ~ skogkategori + treartgruppe9 + beitetrykk9 + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_roads)

rec_r_bin6 <- glmer(recr_bin ~ disthus + distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_roads)

## For this to run, do not scale distvei2 (because of the log())
rec_r_bin7 <- glmer(recr_bin ~ log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = binomial(),
data = recruits_roads) # BEST



```

#### AIC selection bin models
```{r}
library(AICcmodavg)

candmods_rec_roads_bin <- list(rec_r_bin1, rec_r_bin2, rec_r_bin3, rec_r_bin4, rec_r_bin5, rec_r_bin6, rec_r_bin7)
aictab(candmods_rec_roads_bin, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K     AICc Delta_AICc AICcWt Cum.Wt       LL
# Mod7 18 15513.65       0.00      1      1 -7738.80
# Mod2 18 15527.88      14.23      0      1 -7745.91
# Mod1 19 15529.88      16.23      0      1 -7745.91
# Mod4 17 15530.49      16.85      0      1 -7748.23
# Mod3 18 15531.36      17.71      0      1 -7747.65
# Mod6 16 15541.40      27.76      0      1 -7754.68
# Mod5 14 15542.60      28.96      0      1 -7757.29
```

#### Summary bin roads
```{r}
summary(rec_r_bin7)
# vcov(rec_h_bin5)
```



#### Plots bin roads
```{r}
# library(effects)
# 
# plot(allEffects(rec_r_bin7))
# plot(effect("skogkategori", rec_r_bin7))

library(sjPlot)
plot_model(rec_r_bin7, type = "diag")
# plot_model(rec_r_bin7, type = "eff") # Doesn't work...
plot_model(rec_r_bin7, type = "est")

# tab_model(rec_r_bin7, transform = NULL,
#           show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, show.se = TRUE, show.std = NULL, show.p = TRUE, show.stat = FALSE, show.df = FALSE, show.zeroinf = FALSE, show.r2 = TRUE, show.icc = TRUE, show.adj.icc = FALSE, show.re.var = TRUE, show.aic = TRUE, show.dev = FALSE, show.obs = TRUE, p.threshold = c(0.05, 0.01, 0.001))

ggstatsplot::ggcoefstats(
  x = rec_r_bin7,
  title = "generalized linear mixed-effects model"
)

```

#### Save bin roads
```{r}
save(rec_r_bin7, file = "rec_r_bin7.rda")

```




##       Roads beta - Second part of the hurdle, Poisson  ##


## Load data road models
```{r}
load("processdata/recruits_roads.rda")

names(recruits_roads)
```


#### Prepare data set for second part of the hurdle
```{r}
recruits_roads_beta <- recruits_roads[recruits_roads$recruitment > 0, ]
str(recruits_roads_beta)
summary(recruits_roads_beta$recruitment)

is.integer(recruits_roads_beta$recruitment)
recruits_roads_beta$recruitment <- as.integer(recruits_roads_beta$recruitment)
is.integer(recruits_roads_beta$recruitment)

```


#### Scale variables if necessary
```{r}

# recruits_roads_beta$distvei2 <- scale(recruits_roads_beta$distvei2)

recruits_roads_beta$beitetrykk9 <- scale(recruits_roads_beta$beitetrykk9)
recruits_roads_beta$helling <- scale(recruits_roads_beta$helling)
recruits_roads_beta$HOH <- scale(recruits_roads_beta$HOH)
recruits_roads_beta$moose_density <- scale(recruits_roads_beta$moose_density)


```


## Beta roads models
```{r}
library(lme4)
rec_r_beta1 <- glmer(recruitment ~ distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) + moose_density +  ac + (1|KOMNR),
family = poisson(),
data = recruits_roads_beta)
summary(rec_r_beta1)

rec_r_beta2 <- glmer(recruitment ~ distvei2 + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
family = poisson(),
data = recruits_roads_beta)

rec_r_beta3 <- glmer(recruitment ~ skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
family = poisson(),
data = recruits_roads_beta)

## For these models to run, do not scale distvei2
rec_r_beta4 <- glmer(recruitment ~ log(distvei2+1) + skogkategori + treartgruppe9 + beitetrykk9 + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
family = poisson(),
data = recruits_roads_beta)




```


#### AIC selection beta models
```{r}
library(AICcmodavg)

candmods_rec_roads_beta <- list(rec_r_beta1, rec_r_beta2, rec_r_beta3, rec_r_beta4)
aictab(candmods_rec_roads_beta, modnames = NULL,
                       second.ord = TRUE, nobs = NULL, sort = TRUE)

# Model selection based on AICc:
# 
#       K     AICc Delta_AICc AICcWt Cum.Wt        LL
# Mod4 17 570695.8       0.00      1      1 -285330.9
# Mod1 18 571364.0     668.18      0      1 -285663.9
# Mod2 17 571364.4     668.56      0      1 -285665.1
# Mod3 16 571984.2    1288.38      0      1 -285976.1
```


#### Summary beta roads
```{r}
summary(rec_r_beta4)
# vcov(rec_h_bin5)
```



#### Plots beta roads
```{r}
library(effects)

plot(allEffects(rec_r_beta4))
plot(effect("skogkategori", rec_r_beta4))

library(sjPlot)
plot_model(rec_r_beta4, type = "diag")
plot_model(rec_r_beta4, type = "eff") 
plot_model(rec_r_beta4, type = "est")

# tab_model(rec_h_beta4, transform = NULL,
#           show.intercept = TRUE, show.est = TRUE, show.ci = 0.95, show.se = TRUE, show.std = NULL, show.p = TRUE, show.stat = FALSE, show.df = FALSE, show.zeroinf = FALSE, show.r2 = TRUE, show.icc = TRUE, show.adj.icc = FALSE, show.re.var = TRUE, show.aic = TRUE, show.dev = FALSE, show.obs = TRUE, p.threshold = c(0.05, 0.01, 0.001))

ggstatsplot::ggcoefstats(
  x = rec_r_beta4,
  title = "generalized linear mixed-effects model"
)

```


#### Save roads beta model
```{r}
save(rec_r_beta4, file = "rec_r_beta4.rda")
```