---
title: "help_notes"
author: "anne"
date: "18 november 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Maybe install package bestNormalize??

```{r}
# Raises Y to the power of 3
data_dat$trans_Y <- (data_dat$Y)^3      
# Takes the ninth root of Y
data_dat$trans_Y <- (data_dat$Y)^(1/9)  
# Takes the natural logarithm (ln) of Y
data_dat$trans_Y <- log(data_dat$Y)     
# Takes the base-10 logarithm of Y
data_dat$trans_Y <- log10(data_dat$Y)   
# Raises the constant e to the power of Y
data_dat$trans_Y <- exp(data_dat$Y)     
# Finds the absolute value of Y
data_dat$trans_Y <- abs(data_dat$Y)    
# Calculates the sine of Y
data_dat$trans_Y <- sin(data_dat$Y)    
# Calculates the inverse sine (arcsine) of Y
data_dat$trans_Y <- asin(data_dat$Y)   
# Calcuates square root of Y
data_dat$trans1_Y <- sqrt(data_dat$Y)
```



Subset on observations
```{r}
mydata[ which(gender=='F' & age > 65),]
```


### Erlings SSPS analysis:

select if (disthus le 500).
sort cases by takst.
split file by takst.
GENLIN beitetrykk BY landsdel skogkategori treartgruppe kant helling hohkatb (ORDER=ASCENDING) WITH disthus
  /MODEL landsdel skogkategori treartgruppe kant helling hohkatb disthus treartgruppe*disthus skogkategori*disthus INTERCEPT=YES
DISTRIBUTION=NORMAL LINK=IDENTITY
  /CRITERIA SCALE=MLE COVB=MODEL PCONVERGE=1E-006(ABSOLUTE) SINGULAR=1E-012 ANALYSISTYPE=3(WALD) 
    CILEVEL=95 CITYPE=WALD LIKELIHOOD=FULL
  /MISSING CLASSMISSING=EXCLUDE
  /PRINT CPS DESCRIPTIVES MODELINFO FIT SUMMARY SOLUTION.
split file off.

sort cases by takst.
split file by takst.
MIXED beitetrykk BY region treartgruppe skogkategori kant helling hohkatb WITH disthus
  /CRITERIA=CIN(95) MXITER(100) MXSTEP(10) SCORING(1) SINGULAR(0.000000000001) HCONVERGE(0, 
    ABSOLUTE) LCONVERGE(0, ABSOLUTE) PCONVERGE(0.000001, ABSOLUTE)
  /FIXED=treartgruppe skogkategori kant helling disthus hohkatb treartgruppe*disthus skogkategori*disthus | 
    SSTYPE(3)
  /METHOD=REML
  /PRINT=SOLUTION
  /RANDOM=region| COVTYPE(VC).
split file off.


### To test hurdle and zeroinf models
coeftest() and waldtest() from lmtest, as well as linearHypothesis()
from car can be used for Wald tests, and lrtest() from lmtest for LR tests of nested model


