---
title: "09_total_path_effect"
author: "anne"
date: "29 august 2019"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load libraries
```{r}
library(lme4)
library(glmmTMB)
```



## Load data and model
** HOUSE plots: To load the data/ models to make the house plots, load chunks: Browsing pressure - Houses AND Recruits - Houses **
** ROAD plots: To load the data/ models to make the road plots, load chunks: Browsing pressure - Roads AND Recruits - Roads **

# Old
## Browsing pressure
#### Houses
```{r}
# load("output/m1kbin2.rda")
# zeromod1 <- m1kbin2
# Formula: factor(beitetrykkr > 0) ~ disthus_trunc_cut200_scale + log(distvei2 +  
   #  1) + skogkategori + treartgruppe9 + ac_scale + kant + helling +  
   #  HOH_scale + I(HOH_scale^2) + tretetthet9_trunc + (1 | KOMNR)
   # Data: browse9.4_house

# load("output/m1ibeta2.rda")
# percmod1 <- m1ibeta2
# Formula:          bt100 ~ disthus_trunc_cut200_scale + log(distvei2 + 1) + skogkategori +  
#     treartgruppe9 + ac_scale + kant + helling + HOH_scale + I(HOH_scale^2) +  
#     tretetthet9_trunc + (1 | KOMNR)
# Data: browse9.4_house_pos

# load("processdata/browse9.4_house.rda")
# dat1 <- browse9.4_house


```

#### Roads
```{r}
# load("output/m4abin2.rda")
# zeromod1 <- m4abin2
# # summary(zeromod1)
# Formula: factor(beitetrykkr > 0) ~ log(distvei2_trunc + 1) + skogkategori +  
#     treartgruppe9 + ac_scale + kant + helling + HOH_scale + I(HOH_scale^2) +  
#     tretetthet9_trunc + (1 | KOMNR)
#    Data: browse9.4

# load("output/m4abeta2.rda")
# percmod1 <- m4abeta2 
# # summary(percmod1)
# Formula:          bt100 ~ log(distvei2_trunc + 1) + skogkategori + treartgruppe9 +  
#     ac_scale + kant + helling + HOH_scale + I(HOH_scale^2) +      tretetthet9_trunc + (1 | KOMNR)
# Data: browse9.4pos

# load("processdata/browse9.4.rda")
# # head(browse9.4)
# dat1 <- browse9.4



```



## Recruits
#### Houses
```{r}
# load("output/mhusabin.rda")
# zeromod2 <- mhusabin
# 
# # mhusabin <- glmer(factor(proplt > 0) ~ disthus_400 + log(distvei2+1) + skogkategori + treartgruppe9 + browspres_merged + kant + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
# # family = binomial(),
# # data = browse9.5msc)
# 
# load("output/m16abeta_house.rda")
# percmod2 <- m16abeta_house
# 
# # m16beta_house <- glmmTMB(proplt ~ log(distvei2+1) + skogkategori + treartgruppe9 + HOH + I(HOH^2) + browspres_merged + (1|KOMNR),
# #             data = browse9.5mpossc,
# #             family = beta_family())
# 
# load("processdata/browse9.5msc.rda")
# dat2 <- browse9.5msc



```

#### Roads
```{r}
# load("output/m2bin_roads.rda")
# zeromod2 <- m2bin_roads
# # summary(m2bin_roads)
# 
# # m2bin_roads <- glmer(factor(proplt > 0) ~ log(distvei2+1) + skogkategori + treartgruppe9 + browspres_merged + helling + HOH + I(HOH^2) +  ac + (1|KOMNR),
# # family = binomial(),
# # data = browse9.6sc)
# 
# load("output/m3betaroad.rda")
# percmod2 <- m3betaroad
# 
# # m3betaroad <- glmmTMB(proplt ~ skogkategori + treartgruppe9 + ac + helling + HOH + I(HOH^2) + browspres_merged + (1|KOMNR),
# #             data = browse9.6scpos,
# #             family = beta_family())
# 
# load("processdata/browse9.6sc.rda")
# # head(browse9.6sc)
# dat2 <- browse9.6sc


```



# New
## Load HOUSE models data
```{r}
#### Browsing pressure----
load("output/browsing_2021_02_02/browse_h_bin1.rda")
zeromod1 <- browse_h_bin1
summary(zeromod1)

load("output/browsing_2021_02_02/browse_h_beta2.rda")
percmod1 <- browse_h_beta2
summary(percmod1)

load("processdata/browse_house_2021_02_01.rda")
str(browse_house) # Check if variables are scaled, else scale below
# browse_house <- browse_house[ ,-c(4,16:20,22)] #8,

# Scale
browse_house$tretetthet9 <- scale(browse_house$tretetthet9)
browse_house$helling <- scale(browse_house$helling)
browse_house$HOH <- scale(browse_house$HOH)
# browse_house$moose_density <- scale(browse_house$moose_density)
browse_house$disthus_200 <- scale(browse_house$disthus_200)
str(browse_house)

dat1 <- browse_house
head(dat1)


#### Recruitment ----
load("output/recruitment_2021_03_25/rec_h_bin2_600_int2.rda")
zeromod2 <- rec_h_bin2_600_int2
# load("output/recruitment_2021_02_02/rec_h_bin2_600_int.rda")
# zeromod2 <- rec_h_bin2_600_int
# load("output/recruitment_07_12_2020/rec_h_bin2_600_.rda")
# zeromod2 <- rec_h_bin2_600
summary(zeromod2)


load("output/recruitment_2021_03_25/rec_h_beta3_TMB_int2.rda")
percmod2 <- rec_h_beta3_TMB_int2
# load("output/recruitment_2021_02_02/rec_h_beta3_TMB_int.rda")
# percmod2 <- rec_h_beta3_TMB_int
summary(percmod2)

load("processdata/recruits_house_2021_02_02.rda")
str(recruits_house)
# recruits_house <- recruits_house[ ,-c(7)]
recruits_house$recruitment_bin <- ifelse(recruits_house$recruitment == 0, 0, 1)
# scale
# recruits_house$beitetrykk9 <- scale(recruits_house$beitetrykk9)
recruits_house$helling <- scale(recruits_house$helling)
recruits_house$HOH <- scale(recruits_house$HOH)
recruits_house$tretetthet9 <- scale(recruits_house$tretetthet9)
# recruits_house$moose_density <- scale(recruits_house$moose_density)
recruits_house$disthus_600 <- scale(recruits_house$disthus_600)
# recruits_house$disthus_500 <- scale(recruits_house$disthus_500)

is.integer(recruits_house$recruitment)
recruits_house$recruitment <- as.integer(recruits_house$recruitment)
is.integer(recruits_house$recruitment)

str(recruits_house)

dat2 <- recruits_house
head(dat2)

```



## Load ROAD models and data
```{r}
#### Browsing pressure ----
load("output/browsing_2021_02_02/browse_r_bin1.rda")
zeromod1 <- browse_r_bin1
summary(zeromod1)

load("output/browsing_2021_02_02/browse_r_beta2.rda")
percmod1 <- browse_r_beta2 
summary(percmod1)

load("processdata/browse_roads_2021_02_02.rda")
str(browse_roads)
browse_roads$beite_bin <- ifelse(browse_roads$beitetrykk9 == 0, 0, 1)
# Scale
browse_roads$tretetthet9 <- scale(browse_roads$tretetthet9)
browse_roads$helling <- scale(browse_roads$helling)
browse_roads$HOH <- scale(browse_roads$HOH)
# browse_roads$moose_density <- scale(browse_roads$moose_density)
str(browse_roads)

dat1 <- browse_roads
head(dat1)


#### Recruitment ----
load("output/recruitment_2021_03_25/rec_r_bin3_2.rda")
zeromod2 <- rec_r_bin3_2
# load("output/recruitment_2021_02_02/rec_r_bin3.rda")
# zeromod2 <- rec_r_bin3
summary(zeromod2)

load("output/recruitment_2021_03_25/rec_r_beta2_2_TMB.rda")
percmod2 <- rec_r_beta2_2_TMB
# load("output/recruitment_2021_02_02/rec_r_beta2_TMB.rda")
# percmod2 <- rec_r_beta2_TMB
summary(percmod2)

load("processdata/recruits_roads_2021_02_03.rda")
str(recruits_roads)
recruits_roads$recruitment_bin <- ifelse(recruits_roads$recruitment == 0, 0, 1)
is.integer(recruits_roads$recruitment)
recruits_roads$recruitment <- as.integer(recruits_roads$recruitment)
is.integer(recruits_roads$recruitment)
# Scale
# recruits_roads$beitetrykk9 <- scale(recruits_roads$beitetrykk9)
recruits_roads$helling <- scale(recruits_roads$helling)
recruits_roads$HOH <- scale(recruits_roads$HOH)
recruits_roads$tretetthet9 <- scale(recruits_roads$tretetthet9)
# recruits_roads$moose_density <- scale(recruits_roads$moose_density)

dat2 <- recruits_roads
head(dat2)
```




## Load and run function
```{r}
# source("function_resp_curve_08_12_2020_rev_BVM.R")
source("function_resp_curve_08_12_2020_rev_added_browsingvalue.R")
```

#### Select focal variable
```{r}
(focal = c( "disthus", "distvei", "skogkategori", "treartgruppe9", "kant", 
           "helling", "HOH", "tretetthet9", "beitetrykk9", "moose_density")[10])
## REMEMBER to load the road datasets and models after disthus (house model)!!!!!

```

#### Run function for the different models/ focals and SAVE them
hurdle1_only = browsing pressure hurdle
hurdle2_only = recruitment hurdle
total = total effect
```{r}
bp_moose <- resp_curve(focal, dat1, dat2, zeromod1, percmod1, zeromod2, percmod2, 
           which_effect=c("hurdle1_only", "hurdle2_only", "total")[1], nvals=100, plotit=F, nb_btstrp=99)

recruit_moose <- resp_curve(focal, dat1, dat2, zeromod1, percmod1, zeromod2, percmod2,
           which_effect=c("hurdle1_only", "hurdle2_only", "total")[2], nvals=100, plotit=F, nb_btstrp=99)

total_moose <- resp_curve(focal, dat1, dat2, zeromod1, percmod1, zeromod2, percmod2, 
           which_effect=c("hurdle1_only", "hurdle2_only", "total")[3], nvals=100, plotit=F, nb_btstrp=99)

# For interaction, choose between: browsingvalue="max" or "min"
recruit_int_min <- resp_curve(focal, dat1, dat2, zeromod1, percmod1, zeromod2, percmod2, 
           which_effect=c("hurdle1_only", "hurdle2_only", "total")[2], nvals=100, plotit=F, nb_btstrp=99, browsingvalue = "min")
recruit_int_max <- resp_curve(focal, dat1, dat2, zeromod1, percmod1, zeromod2, percmod2, 
           which_effect=c("hurdle1_only", "hurdle2_only", "total")[2], nvals=100, plotit=F, nb_btstrp=99, browsingvalue = "max")
```

#### Save function data!
```{r}
save(bp_moose, file = "output/function_results_2021_02_03/bp_moose.rda")

save(recruit_int_max, file = "output/function_results_2021_03_25/recruit_int_max.rda")

save(recruit_tretett, file = "output/function_results_2021_03_25/house/recruit_tretett.rda")
save(total_tretett, file = "output/function_results_2021_03_25/house/total_tretett.rda") 
 
```




## load function data (These are the final function outputs)
```{r}
# Browsing pressure (indirect)
load("output/function_results_2021_02_03/bp_disthus.rda")
load("output/function_results_2021_02_03/bp_distvei.rda")
load("output/function_results_2021_02_03/bp_skogkat.rda")
load("output/function_results_2021_02_03/bp_kant.rda")
load("output/function_results_2021_02_03/bp_treart.rda")
load("output/function_results_2021_02_03/bp_helling.rda")
load("output/function_results_2021_02_03/bp_HOH.rda")
load("output/function_results_2021_02_03/bp_tretett.rda")
load("output/function_results_2021_02_03/bp_moose.rda")

# Recruits (direct)
# load("output/function_results_2021_02_03/recruit_disthus.rda")
load("output/function_results_2021_03_25/recruit_int_min.rda")
load("output/function_results_2021_03_25/recruit_int_max.rda")
load("output/function_results_2021_03_25/recruit_distvei.rda")
load("output/function_results_2021_03_25/recruit_skogkat.rda")
load("output/function_results_2021_03_25/recruit_kant.rda")
load("output/function_results_2021_03_25/recruit_treart.rda")
load("output/function_results_2021_03_25/recruit_helling.rda")
load("output/function_results_2021_03_25/recruit_beite.rda")
load("output/function_results_2021_03_25/recruit_HOH.rda")
load("output/function_results_2021_03_25/recruit_moose.rda")
load("output/function_results_2021_03_25/recruit_tretett.rda")

# Total (indirect + direct)
# load("output/function_results_2021_03_25/total_disthus.rda")
load("output/function_results_2021_03_25/total_distvei.rda")
load("output/function_results_2021_03_25/total_skogkat.rda")
load("output/function_results_2021_03_25/total_kant.rda")
load("output/function_results_2021_03_25/total_treart.rda")
load("output/function_results_2021_03_25/total_helling.rda")
load("output/function_results_2021_03_25/total_beite.rda")
load("output/function_results_2021_03_25/total_tretett.rda")
load("output/function_results_2021_03_25/total_HOH.rda")
load("output/function_results_2021_03_25/total_moose.rda")

```


## Re-scale (NOT when using loaded function outputs!!!)
```{r}
# d$s.x * attr(d$s.x, 'scaled:scale') + attr(d$s.x, 'scaled:center')


## Browse (hurdle1)

### House

# attributes(browse_house$disthus_200) # $`scaled:center` 192.2636 $`scaled:scale` 27.71453
bp_disthus$var <- bp_disthus$var * 27.71453 + 192.2636


### Roads

# attributes(browse_roads$helling) # $`scaled:center` 19.83571 $`scaled:scale` 20.63004
# attributes(browse_roads$HOH) # $`scaled:center` 378.861 $`scaled:scale` 243.1602
# attributes(browse_roads$moose_density) # $`scaled:center` 0.2775515 $`scaled:scale` 0.2047208
# attributes(browse_roads$tretetthet9) # $`scaled:center` 993.2908 $`scaled:scale` 1152.076
bp_helling$var <- bp_helling$var * 20.63004 + 19.83571
bp_HOH$var <- as.integer(bp_HOH$var * 243.1602 + 378.861) # for some reason I got scientific notation here, solves by using as.integer
# bp_moose$var <- bp_moose$var * 0.2047208 + 0.2775515
bp_tretett$var <- bp_tretett$var * 1152.076 + 993.2908

bp_distvei$var <- exp(bp_distvei$var)-1




## Recruitment (hurdle2)

### House

# attributes(recruits_house$disthus_600) # $`scaled:center` 499.182 $`scaled:scale` 162.9665
recruit_disthus$var <- recruit_disthus$var * 162.9665 + 499.182
recruit_int_min$var <- recruit_int_min$var * 162.9665 + 499.182
recruit_int_max$var <- recruit_int_max$var * 162.9665 + 499.182

# attributes(recruits_house$helling) # $`scaled:center` 19.68501 $`scaled:scale` 20.08128
# attributes(recruits_house$HOH) # $`scaled:center` 365.9363 $`scaled:scale` 245.9447
# attributes(recruits_house$tretetthet9) # $`scaled:center` 1043.477 $`scaled:scale` 1308.988
recruit_tretett$var <- recruit_tretett$var * 1308.988 + 1043.477
recruit_hell$var <- recruit_hell$var * 20.08128 + 19.68501
recruit_HOH$var <- as.integer(recruit_HOH$var * 245.9447 + 365.9363)


### Roads

# attributes(recruits_roads$beitetrykk9) # $`scaled:center` 26.01752 $`scaled:scale` 30.81325
# attributes(recruits_roads$helling) # $`scaled:center` 19.10349 $`scaled:scale` 19.60225
# attributes(recruits_roads$HOH) # $`scaled:center` 365.9363 $`scaled:scale` 245.9447
# attributes(recruits_roads$moose_density) # $`scaled:center` 0.2841981 $`scaled:scale` 0.1988112
# recruit_bp$var <- recruit_bp$var * 30.81325 + 26.01752
recruit_helling$var <- recruit_helling$var * 19.60225 + 19.10349
recruit_HOH$var <- as.integer(recruit_HOH$var * 245.9447 + 365.9363)
recruit_tretett$var <- recruit_tretett$var * 1193.3 + 984.6252
# recruit_moose$var <- recruit_moose$var * 0.1988112 + 0.2841981

recruit_distvei$var <- exp(recruit_distvei$var)-1






## Total 

### House
total_disthus$var <- total_disthus$var * 162.9665 + 499.182
recruit_int_min2$var <- recruit_int_min2$var * 162.9665 + 499.182
recruit_int_max2$var <- recruit_int_max2$var * 162.9665 + 499.182

total_tretett$var <- total_tretett$var * 1308.988 + 1043.477
total_hell$var <- total_hell$var * 20.08128 + 19.68501
total_HOH$var <- as.integer(total_HOH$var * 245.9447 + 365.9363)
total_distvei$var <- exp(total_distvei$var)-1

### Roads
# attributes(recruits_roads$tretetthet9) # $`scaled:center` 984.6252 $`scaled:scale` 1193.3
total_helling$var <- total_helling$var * 19.60225 + 19.10349
total_HOH$var <- as.integer(total_HOH$var * 245.9447 + 365.9363)
total_tretett$var <- total_tretett$var * 1193.3 + 984.6252
total_moose$var <- total_moose$var * 0.1988112 + 0.2841981

total_distvei$var <- exp(total_distvei$var)-1


# # disthus
# bp_disthus$var <- bp_disthus$var * 27.71453 + 192.2636
# 
# recruit_disthus$var <- recruit_disthus$var * 88.52122 + 358.5594
# total_disthus$var <- total_disthus$var * 88.52122 + 358.5594 
# 
# # road models
# bp_distvei$var <- exp(bp_distvei$var)-1
# bp_hoh$var <- bp_hoh$var * 244.7748 + 361.8423
# 
# 
# recruit_distvei$var <- exp(recruit_distvei$var)-1
# recruit_HOH$var <- recruit_HOH$var * 244.7748 + 361.8423
# 
# 
# total_distvei$var <- exp(total_distvei$var)-1
# total_HOH$var <- total_HOH$var * 244.7748 + 361.8423

```




## Plots
** pdt = Plot Direct and Total effects recruits, pt = Plot Total effects only recruits, pd = Plot Direct effects only recruits, ph = Plot Hurdle (browsing pressure) **

```{r}
# load ggplot library ----
library(ggplot2)

# colour blind friendly palettes:
# The palette with grey:
cbPalette <- c("#999999", "#009E73", "#56B4E9", "#E69F00", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
# The palette with black:
# cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# To use for fills, add
  # scale_fill_manual(values=cbPalette)

# To use for line and point colors, add
  # scale_colour_manual(values=cbPalette)

  
  
# disthus ----
# pdt_disthus <- ggplot() + 
#   geom_ribbon(data = recruit_disthus, aes(x = var, ymin = CI025, ymax = CI975), 
#               linetype = 0, alpha = 0.2, show.legend = F) +
#   geom_line(data = recruit_disthus, aes(var, point, 
#                                         color = "direct", 
#                                         linetype = "direct"),
#             size = 1.5, show.legend = T) +
#   
#   geom_line(data = total_disthus, aes(var, point, color = "total", linetype = "total"), 
#             size = 1.5, show.legend = T) +
#   geom_ribbon(data = total_disthus, aes(x = var, ymin = CI025, ymax = CI975), 
#               fill = "#009E73", linetype = 0, alpha = 0.2, show.legend = F) +
#   
#   scale_linetype_manual("Effect",
#                         values = c("direct" = 3,"total" = 1)) +
#   xlab("\nDistance to house (m)") + 
#   ylab("Recruitment (ha 10yr)") +
#   theme_light()+
#   theme(axis.text = element_text(size = 20), # face = "bold"
#         axis.title = element_text(family = "sans", size = 25),
#         legend.position = c(0.8, 0.85),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)) +
#   scale_color_manual(name = "Effect", 
#                      values = cbPalette) +
#     scale_fill_manual(values = "#009E73")
#,legend.title = element_text(size = 50)


# pt_disthus <- ggplot() + 
#   geom_line(data = total_disthus, aes(var, point, color = "total"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = total_disthus, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nDistance to house (m)") + 
#   ylab("Recruitment (ha 10yr) (ha 10yr)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruitment (ha 10yr) (ha 10yr)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))
# 

# pt_disthus <- ggplot() +
#   geom_ribbon(data = recruit_int_min2, aes(x = var, ymin = CI025, ymax = CI975), linetype = 0, alpha = 0.2, show.legend = F)+ 
#   geom_line(data = recruit_int_min2, aes(var, point, colour = "low", linetype = "low"),  size = 1.5, show.legend = T) +
#   geom_ribbon(data = recruit_int_max2, aes(x = var, ymin = CI025, ymax = CI975), linetype = 0, alpha = 0.2, show.legend = F) +
#   geom_line(data = recruit_int_max2, aes(var, point, colour = "high", linetype = "high"), size = 1.5, show.legend = T) + 
#   scale_linetype_manual("Browsing pressure",
#                         values = c("low" = 1,"high" = 1)) +
#   xlab("\nDistance to house (m)") + 
#   ylab("Recruitment (ha 10yr)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 20), # face = "bold"
#         axis.title = element_text(family = "sans", size = 25),
#         legend.position = c(0.8, 0.85),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)) +
#   scale_color_manual(name = "Browsing pressure", 
#                      values = c("low" = "red", "high" = "blue")) +
#     scale_fill_manual(values = "#009E73")



pd_disthus <- ggplot() +
  geom_ribbon(data = recruit_int_min, aes(x = var, ymin = CI025, ymax = CI975), linetype = 3, alpha = 0.2, show.legend = F)+ 
  geom_line(data = recruit_int_min, aes(var, point, colour = "low", linetype = "low"),  size = 1.5, show.legend = T) +
  geom_ribbon(data = recruit_int_max, aes(x = var, ymin = CI025, ymax = CI975), fill = "#999999", linetype = 3, alpha = 0.2, show.legend = F) +
  geom_line(data = recruit_int_max, aes(var, point, colour = "high", linetype = "high"), size = 1.5, show.legend = T) + 
  scale_linetype_manual("Browsing pressure",
                        values = c("low" = 3,"high" = 3), guide = guide_legend(reverse=TRUE)) +
  xlab("\nDistance to house (m)") + 
  ylab("Recruitment (ha 10yr)\n") +
  theme_light()+
  theme(axis.text = element_text(size = 20), # face = "bold"
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.8, 0.85),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  scale_color_manual(name = "Browsing pressure", 
                     values = c("low" = "#56B4E9", "high" = "#0072B2"), guide = guide_legend(reverse=TRUE)) +
    scale_fill_manual(values = "#999999")



# pd_disthus <- ggplot() +
#   geom_line(data = recruit_disthus, aes(var, point, color = "direct"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = recruit_disthus, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nDistance to house (m)") +
#   ylab("Recruitment (ha 10yr)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruitment (ha 10yr)",
#                      values = c("total" = "#009292", "direct" = "#004949"))


ph_disthus <- ggplot() +
  geom_ribbon(data = bp_disthus, aes(x = var, ymin = CI025, ymax = CI975), show.legend = F, 
              fill = "#0072B2", linetype = 0, alpha = 0.2) + 
  geom_line(data = bp_disthus, aes(var, point),colour = "#0072B2", linetype = 1, size = 1.5)+
  theme_light() +
  theme(axis.text = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Distance to house (m)\n") + 
  ylab("Browsing pressure (%)\n") +
    scale_fill_manual(values = "#0072B2")

# distvei ----
pdt_distvei <- ggplot() + 
  geom_ribbon(data = recruit_distvei, aes(x = var, ymin = CI025, ymax = CI975), 
              linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = recruit_distvei, aes(var, point, 
                                        color = "direct", 
                                        linetype = "direct"),
            size = 1.5, show.legend = T) +
  
  geom_line(data = total_distvei, aes(var, point, color = "total", linetype = "total"), 
            size = 1.5, show.legend = T) +
  geom_ribbon(data = total_distvei, aes(x = var, ymin = CI025, ymax = CI975), 
              fill = "#009E73", linetype = 0, alpha = 0.2, show.legend = F) +
  
  scale_linetype_manual("Effect",
                        values = c("direct" = 3,"total" = 1)) +
  xlab("\nDistance to road (m)") + 
  ylab("Recruitment (ha 10yr)\n") +
  theme_light()+
  theme(axis.text = element_text(size = 20), # face = "bold"
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.8, 0.85),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  scale_color_manual(name = "Effect", 
                     values = cbPalette) +
    scale_fill_manual(values = "#009E73")
#,legend.title = element_text(size = 50)

# pt_distvei <- ggplot() + 
#   geom_line(data = total_distvei, aes(var, point, color = "total"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = total_distvei, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nDistance to road (m)") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))
# 
# pd_distvei <- ggplot() + 
#   geom_line(data = recruit_distvei, aes(var, point, color = "direct"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = recruit_distvei, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nDistance to road (m)") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))

ph_distvei <- ggplot() +
  geom_ribbon(data = bp_distvei, aes(x = var, ymin = CI025, ymax = CI975), show.legend = F, 
              fill = "#0072B2", linetype = 0, alpha = 0.2) + 
  geom_line(data = bp_distvei, aes(var, point),colour = "#0072B2", linetype = 1, size = 1.5)+
  theme_light() +
  theme(axis.text = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Distance to road (m)\n") + 
  ylab("Browsing pressure (%)\n") +
    scale_fill_manual(values = "#0072B2")



# skogkat ----
pdt_skogkat <- ggplot() +
  geom_pointrange(data = recruit_skogkat, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "direct"), size = 1, position = position_nudge(0.1, 0.1)) +
  theme_light() +
  
  geom_pointrange(data = total_skogkat, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "total"), size = 1, position = position_nudge(-0.1, -0.1)) +
  
  theme(axis.text.x = element_text(size = 18, angle = 35, vjust = 0.5, hjust = 0.5), # face = "bold"
        axis.text.y = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.85, 0.75),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  xlab("Forest category") + 
  ylab("Recruitment (ha 10yr)\n") +
  scale_x_discrete(labels = c("High-prod. \nold forest", "High-prod. \nyoung forest", "Low-prod. \nold forest", "Low-prod. \nyoung forest", "Unproductive \nforest"))+
   scale_color_manual(name = "Effect", 
                     values = cbPalette)


# pt_skogkat <- ggplot() +
#   geom_pointrange(data = total_skogkat, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "total"), size = 1) +
#   theme_light() +
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   xlab("\nForest category") + 
#   ylab("Recruits (%)\n") +
#   scale_x_discrete(labels = c("Highproductive \nold forest", "Highproductive \nyoung forest", "Lowproductive \nold forest", "Lowproductive \nyoung forest", "Unproductive \nforest"))+
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))
# 
# pd_skogkat <- ggplot() +
#   geom_pointrange(data = recruit_skogkat, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "direct"), size = 1) +
#   theme_light() +
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   xlab("\nForest category") + 
#   ylab("Recruits (%)\n") +
#   scale_x_discrete(labels = c("Highproductive \nold forest", "Highproductive \nyoung forest", "Lowproductive \nold forest", "Lowproductive \nyoung forest", "Unproductive \nforest"))+
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))


ph_skogkat <- ggplot(data = bp_skogkat,aes(var, point)) +
  geom_pointrange(aes(ymin = CI025, ymax = CI975), colour = "#0072B2", size = 1.5) +
  theme_light() +
  theme(axis.text.x = element_text(size = 18, angle = 35, vjust = 0.5, hjust = 0.5),
        axis.text.y = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Forest category\n") + 
  ylab("Browsing pressure (%)\n") +
  scale_x_discrete(labels = c("High-prod. \nold forest", "High-prod. \nyoung forest", "Low-prod. \nold forest", "Low-prod. \nyoung forest", "Unproductive \nforest")) 


# treart ----
pdt_treart <- ggplot() +
  geom_pointrange(data = recruit_treart, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "direct"), size = 1, position = position_nudge(0.1, 0.1)) +
  
  geom_pointrange(data = total_treart, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "total"), size = 1, position = position_nudge(-0.1, -0.1)) +
  
  theme_light() +
  theme(axis.text.x = element_text(size = 20, angle = 30, vjust = 0.5, hjust = 0.5), # face = "bold"
        axis.text.y = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.85, 0.8),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  xlab("Tree species group\n") + 
  ylab("") +
  scale_x_discrete(labels = c("Pine", "Other deciduous \ntrees", "Rowan, aspen, \nwillow")) +
  scale_color_manual(name = "Effect", 
                     values = cbPalette)


# pt_treart <- ggplot() +
#   geom_pointrange(data = total_treart, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "total"), size = 1) +
#   theme_light() +
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   xlab("\nTree species group") + 
#   ylab("Recruits (%)\n") +
#   scale_x_discrete(labels = c("Pine", "Other deciduous \ntrees", "Rowan, aspen, \nwillow")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))
# 
# pd_treart <- ggplot() +
#   geom_pointrange(data = recruit_treart, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "direct"), size = 1) +
#   theme_light() +
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   xlab("\nTree species group") + 
#   ylab("Recruits (%)\n") +
#   scale_x_discrete(labels = c("Pine", "Other deciduous \ntrees", "Rowan, aspen, \nwillow")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))


ph_treart <- ggplot(data = bp_treart,aes(var, point)) +
  geom_pointrange(aes(ymin = CI025, ymax = CI975), colour = "#0072B2", size = 1.5) +
  theme_light() +
  theme(axis.text.x = element_text(size = 20, angle = 35, vjust = 0.5, hjust = 0.5),
        axis.text.y = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Tree species groups\n") + 
  ylab("") +
  scale_x_discrete(labels = c("Pine", "Other deciduous \ntrees", "Rowan, aspen, \nwillow")) 

# kant ----
pdt_kant <- ggplot() +
  geom_pointrange(data = recruit_kant, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "direct"), size = 1, position = position_nudge(0.1, 0.1)) +
  
  geom_pointrange(data = total_kant, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "total"), size = 1, position = position_nudge(-0.1, -0.1)) +
  
  theme_light() +
  theme(axis.text.x = element_text(size = 20, angle = 35, vjust = 0.5, hjust = 0.5), # face = "bold"
        axis.text.y = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.85, 0.75),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  xlab("Edge effect\n") +
  ylab("") +
  scale_x_discrete(labels = c("Edge <10m", "Edge >20m", "Edge 10-20m", "Edge \nmissing")) +
  scale_color_manual(name = "Effect", 
                     values = cbPalette)


# pd_kant <- ggplot() +
#   geom_pointrange(data = recruit_kant, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "direct"), size = 1) +
#   theme_light() +
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   xlab("\nEdge effect") + 
#   ylab("Recruitment (ha 10yr) (ha 10yr)\n") +
#   scale_x_discrete(labels = c("Edge <10m", "Edge >20m", "Edge 10-20m", "Edge information\nmissing"))
# 
# 
# pt_kant <- ggplot() +
#   geom_pointrange(data = total_kant, aes(x = var, y = point, ymin = CI025, ymax = CI975, colour = "indirect"), size = 1) +
#   theme_light() +
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   xlab("\nEdge effect") + 
#   ylab("Recruitment (ha 10yr) (ha 10yr)\n") +
#   scale_x_discrete(labels = c("Edge <10m", "Edge >20m", "Edge 10-20m", "Edge information\nmissing")) +
#   scale_color_manual(name = "Effect on \nRecruitment (ha 10yr) (ha 10yr)", 
#                      values = c("indirect" = "#009292", "direct" = "#004949"))


ph_kant <- ggplot(data = bp_kant, aes(var, point)) +
  geom_pointrange(aes(ymin = CI025, ymax = CI975), colour = "#0072B2", size = 1.5) +
  theme_light() +
  theme(axis.text.x = element_text(size = 20, angle = 35, vjust = 0.5, hjust = 0.5),
        axis.text.y = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Edge effect\n") + 
  ylab("") +
  scale_x_discrete(labels = c("Edge \n<10m", "Edge \n>20m", "Edge \n10-20m", "Edge \nmissing"))

# hell ----
pdt_hell <- ggplot() + 
  geom_ribbon(data = recruit_hell, aes(x = var, ymin = CI025, ymax = CI975), 
              linetype = 0, alpha = 0.2, show.legend = F) +  
  geom_line(data = recruit_hell, aes(var, point, color = "direct", linetype = "direct"), 
            size = 1.5, show.legend = T) +
  
  geom_ribbon(data = total_hell, aes(x = var, ymin = CI025, ymax = CI975), fill = "#009E73", linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = total_hell, aes(var, point, color = "total", linetype = "total"), 
            size = 1.5, show.legend = T) +
  
  scale_linetype_manual("Effect",
                        values = c("direct" = 3,"total" = 1)) +
  xlab("Slope (%)\n") +
  ylab("Recruitment (ha 10yr)\n") +
  theme_light()+
  theme(axis.text = element_text(size = 20), # face = "bold"
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.2, 0.75),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  scale_color_manual(name = "Effect", 
                     values = cbPalette) +
    scale_fill_manual(values = "#009E73")


# pt_hell <- ggplot() + 
#   geom_line(data = total_helling, aes(var, point, color = "total"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = total_helling, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nSlope (%)") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))
# 
# pd_hell <- ggplot() + 
#   geom_line(data = recruit_helling, aes(var, point, color = "direct\n(only on\nprobability)"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = recruit_helling, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nSlope (%)") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct\n(only on\nprobability)" = "#004949"))


ph_hell <- ggplot() +
  geom_ribbon(data = bp_helling, aes(x = var, ymin = CI025, ymax = CI975), show.legend = F, 
              fill = "#0072B2", linetype = 0, alpha = 0.2) + 
  geom_line(data = bp_helling, aes(var, point),colour = "#0072B2", linetype = 1, size = 1.5)+
  theme_light() +
  theme(axis.text = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Slope (%)\n") + 
  ylab("") +
    scale_fill_manual(values = "#0072B2")


# hoh ----
pdt_hoh <- ggplot() + 
  geom_ribbon(data = recruit_HOH, aes(x = var, ymin = CI025, ymax = CI975), 
              linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = recruit_HOH, aes(var, point, color = "direct", linetype = "direct"), 
            size = 1.5, show.legend = T) +
  
  geom_ribbon(data = total_HOH, aes(x = var, ymin = CI025, ymax = CI975), fill = "#009E73", linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = total_HOH, aes(var, point, color = "total", linetype = "total"), 
            size = 1.5, show.legend = T) +
  
  scale_linetype_manual("Effect",
                        values = c("direct" = 3,"total" = 1)) +
  
  xlab("Altitude (masl)\n") + 
  ylab("") +
  theme_light()+
  theme(axis.text = element_text(size = 20), # face = "bold"
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.2, 0.75),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  scale_color_manual(name = "Effect", 
                     values = cbPalette) +
    scale_fill_manual(values = "#009E73")


# pt_hoh <- ggplot() + 
#   geom_line(data = total_hoh, aes(var, point, color = "total"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = total_hoh, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nAltitude (masl)") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))
# 
# pd_hoh <- ggplot() + 
#   geom_line(data = recruit_hoh, aes(var, point, color = "direct"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = recruit_hoh, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nAltitude (masl)") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))


ph_hoh <- ggplot() +
  geom_ribbon(data = bp_HOH, aes(x = var, ymin = CI025, ymax = CI975), show.legend = F, 
              fill = "#0072B2", linetype = 0, alpha = 0.2) + 
  geom_line(data = bp_HOH, aes(var, point),colour = "#0072B2", linetype = 1, size = 1.5)+
  theme_light() +
  theme(axis.text = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Altitude (masl)\n") + 
  ylab("Browsing pressure (%)\n") +
    scale_fill_manual(values = "#0072B2")


# tretett ----
pdt_tretett <- ggplot() + 
  geom_ribbon(data = recruit_tretett, aes(x = var, ymin = CI025, ymax = CI975), 
              linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = recruit_tretett, aes(var, point, color = "direct", linetype = "direct"), 
            size = 1.5, show.legend = T) +
  
  geom_ribbon(data = total_tretett, aes(x = var, ymin = CI025, ymax = CI975), fill = "#009E73", linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = total_tretett, aes(var, point, color = "total", linetype = "total"), 
            size = 1.5, show.legend = T) +
  
  scale_linetype_manual("Effect",
                        values = c("direct" = 3,"total" = 1)) +
  
  xlab("Tree density (ha)\n") + 
  ylab("") +
  theme_light()+
  theme(axis.text = element_text(size = 20), # face = "bold"
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.2, 0.75),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  scale_color_manual(name = "Effect", 
                     values = cbPalette) +
    scale_fill_manual(values = "#009E73")

# pt_tretett <- ggplot() + 
#   geom_line(data = total_tretett, aes(var, point, color = "indirect"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = total_tretett, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nTree density") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 14),
#         axis.title = element_text(family = "sans", size = 20),
#         legend.position = "bottom",
#         legend.text = element_text(size = 14),
#         legend.title = element_text(size = 14)) +
#   scale_color_manual(name = "Effect on Recruits (%)", 
#                      values = c("indirect" = "#009292", "direct" = "#004949"))


ph_tretett <- ggplot() +
  geom_ribbon(data = bp_tretett, aes(x = var, ymin = CI025, ymax = CI975), show.legend = F, 
              fill = "#0072B2", linetype = 0, alpha = 0.2) + 
  geom_line(data = bp_tretett, aes(var, point),colour = "#0072B2", linetype = 1, size = 1.5)+
  theme_light() +
  theme(axis.text.x = element_text(size = 18), 
        axis.text.y = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Tree density (ha)\n") + 
  ylab("Browsing pressure (%)\n") +
    scale_fill_manual(values = "#0072B2")


# beite ----
pdt_beite <- ggplot() + 
  geom_ribbon(data = recruit_beite, aes(x = var, ymin = CI025, ymax = CI975), 
              linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = recruit_beite, aes(var, point, color = "direct", linetype = "direct"), 
            size = 1.5, show.legend = T) +
  
  scale_linetype_manual("Effect",
                        values = c("direct" = 3)) +
  xlab("Browsing pressure (%)\n") + 
  ylab("") +
  theme_light()+
  theme(axis.text = element_text(size = 20), # face = "bold"
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  scale_color_manual(name = "Effect", 
                     values = cbPalette) +
    scale_fill_manual(values = cbPalette)


# pt_beite <- ggplot() + 
#   geom_line(data = recruit_bp, aes(var, point, color = "direct"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = recruit_bp, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nBrowsing pressure (%)") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))

# pd_beite <- ggplot() + 
#   geom_line(data = recruit_beite, aes(var, point, color = "direct"), linetype = 1, size = 1, show.legend = T) +
#   geom_ribbon(data = recruit_beite, aes(x = var, ymin = CI025, ymax = CI975), colour = "#004949", linetype = 2, alpha = 0.2) +
#   xlab("\nBrowsing pressure (%)") + 
#   ylab("Recruits (%)\n") +
#   theme_light()+
#   theme(axis.text = element_text(size = 10),
#         axis.title = element_text(family = "sans", size = 14, color = "grey30")) +
#   scale_color_manual(name = "Effect on \nRecruits (%)", 
#                      values = c("total" = "#009292", "direct" = "#004949"))


# moose_density ----

pdt_moose <- ggplot() + 
  geom_ribbon(data = recruit_moose, aes(x = var, ymin = CI025, ymax = CI975), 
              linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = recruit_moose, aes(var, point, color = "direct", linetype = "direct"), 
            size = 1.5, show.legend = T) +
  
  geom_ribbon(data = total_moose, aes(x = var, ymin = CI025, ymax = CI975), fill = "#009E73", linetype = 0, alpha = 0.2, show.legend = F) +
  geom_line(data = total_moose, aes(var, point, color = "total", linetype = "total"), 
            size = 1.5, show.legend = T) +
  scale_linetype_manual("Effect",
                        values = c("direct" = 3,"total" = 1)) +
  xlab("Moose density (5 yr mean)\n") + 
  ylab("") +
  theme_light()+
  theme(axis.text = element_text(size = 20), # face = "bold"
        axis.title = element_text(family = "sans", size = 25),
        legend.position = c(0.8, 0.75),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)) +
  scale_color_manual(name = "Effect", 
                     values = cbPalette) +
    scale_fill_manual(values = "#009E73")



ph_moose <- ggplot() +
  geom_ribbon(data = bp_moose, aes(x = var, ymin = CI025, ymax = CI975), show.legend = F, 
              fill = "#0072B2", linetype = 0, alpha = 0.2) + 
  geom_line(data = bp_moose, aes(var, point),colour = "#0072B2", linetype = 1, size = 1.5)+
  theme_light() +
  theme(axis.text = element_text(size = 20),
        axis.title = element_text(family = "sans", size = 25)) +
  xlab("Moose density (5 yr mean)\n") + 
  ylab("") +
    scale_fill_manual(values = "#0072B2")



```
#### Plotgrid
```{r}

library(gridExtra)
library(egg)
library(cowplot)
library(grid)

## !! For high resolution figures either increase dpi to 300-600 or use .pdf instead of .tiff. 300-600 dpi figures will be very large in terms of MB

## browsing pressure #############

# disthus
nullplot <- ggplot()+
  theme_void()
hurdle_husvei <- ggarrange(nullplot, ph_disthus,
          ncol = 1,
          nrow = 2,
          heights = c(0.1,1),
          label.args = list(gp = gpar(font = 2, fontsize = 15), x = unit(1,"line"), hjust = -1, vjust = 0),
          widths = c(1),
          draw = F
          )
ggsave(file = "figs_tabs/total_direct_function/2021_03_03/function_browse_hurdle_hus.tiff", hurdle_husvei, width = 15, height = 15, units = "cm", dpi = 150) #, dpi = 150

# rest
nullplot <- ggplot()+
  theme_void()

hurdle_grid <- ggarrange(nullplot, nullplot, ph_distvei, ph_treart, ph_skogkat, ph_kant, ph_tretett, ph_hell, ph_hoh, ph_moose,
          ncol = 2,
          nrow = 5,
          heights = c(0.2,1, 1, 1, 1),# 0.2
          labels = c("","","(a)", "(b)", "(c)", "(d)","(e)", "(f)","(g)","(h)"),
          label.args = list(gp = gpar(font = 2, fontsize = 15), x = unit(1,"line"), hjust = -2.5, vjust = -1),
          widths = c(1,1),# 0.1
          draw = F
          )
ggsave(file = "figs_tabs/total_direct_function/2021_03_03/function_browse_hurdle_grid_0303.pdf", hurdle_grid, width = 30, height = 45, units = "cm") #, dpi = 150

 


## total/direct ##############
nullplot <- ggplot()+
  theme_void()
total_direct_husvei <- ggarrange(nullplot, pd_disthus, 
          ncol = 1,
          nrow = 2,
          heights = c(0.1,1),
          label.args = list(gp = gpar(font = 2, fontsize = 15), x = unit(1,"line"), hjust = -1, vjust = 0),
          widths = c(1),
          draw = F
          )
ggsave(file = "figs_tabs/total_direct_function/2021_03_25/function_total_direct_hus_int.tiff", total_direct_husvei, width = 15, height = 15, units = "cm", dpi = 150) #, dpi = 150

# rest
nullplot <- ggplot()+
  theme_void()

total_direct_grid <- ggarrange(nullplot, nullplot, nullplot, nullplot, pdt_distvei, pdt_beite, pdt_treart, nullplot, pdt_skogkat, pdt_kant,  pdt_hoh, nullplot, pdt_hell,  pdt_moose, pdt_tretett, nullplot,
          ncol = 4,
          nrow = 4,
          heights = c(0.2,1, 1, 1),
          labels = c("","", "", "", "(a)", "(b)", "(c)", "", "(d)", "(e)", "(f)", "", "(g)", "(h)", "(i)",""),
          label.args = list(gp = gpar(font = 2, fontsize = 15), x = unit(1,"line"), hjust = -2.5, vjust = -1),
          widths = c(1,1,1, 0.1),
          draw = F
          )
ggsave(file = "figs_tabs/total_direct_function/2021_03_25/function_total_direct_grid_0303.tiff", total_direct_grid, width = 40, height = 40, units = "cm", dpi = 150) #, dpi = 150


total_direct_grid <- ggarrange(nullplot, nullplot, nullplot, pdt_treart, pdt_skogkat, pdt_kant,  pdt_hoh, pdt_hell,  pdt_moose, pdt_tretett,
          ncol = 3,
          nrow = 4,
          heights = c(0.2, 1, 1, 1),
          labels = c(), #"","", "", "", "(a)", "(b)", "(c)", "", "(d)", "(e)", "(f)", "", "(g)", "(h)", "(i)",""
          label.args = list(gp = gpar(font = 2, fontsize = 15), x = unit(1,"line"), hjust = -2.5, vjust = -1),
          widths = c(1,1,1),
          draw = F
          )
ggsave(file = "figs_tabs/total_direct_function/2021_03_25/function_total_direct_grid_house.tiff", total_direct_grid, width = 40, height = 40, units = "cm", dpi = 150) #, dpi = 150

```




## Figures data forest category and tree species group for the results/ appendix
```{r}
library(ggplot2)
load("processdata/browse_roads_2021_02_02.rda")
str(browse_roads)

fp1 <- ggplot(data = browse_roads, aes(treartgruppe9)) +
  geom_bar()+
  theme_light()+
  scale_x_discrete(labels = c("pine", "deciduous \ntrees", "RAW")) +
  xlab("\nTree species groups") + 
  ylab("Count\n")

fp2 <- ggplot(data = browse_roads, aes(skogkategori)) +
  geom_bar()+
  theme_light()+
  scale_x_discrete(labels = c("Lowproductive \nold forest", "Highproductive \nold forest", "Highproductive \nyoung forest", "Lowproductive \nyoung forest", "Unproductive \nforest")) +
  xlab("\nForest category") + 
  ylab("Count\n")


library(gridExtra)
fp_grid <- grid.arrange(fp1, fp2,
          nrow = 2, ncol = 1)

ggsave(file = "fp_grid.tiff", fp_grid, width = 15, height = 30, units = "cm", dpi = 150) #, dpi = 150
```




## min, max, se and more of some variables
```{r}
library(psych)
load("processdata/recruits_roads_2021_02_03.rda")
str(recruits_roads)

describe(browse_roads$beitetrykk9)
describe(recruits_roads$recruitment)

```



## % of plots within 200m from roads/ houses (for how much of the forest lies within these areas)
```{r}
## Browsing
load("processdata/browse_house_2021_02_01.rda")
length(levels(as.factor(browse_house$FLATEID))) # total 11561
length(levels(as.factor(browse_house$FLATEID[browse_house$distvei2 <= "200"]))) # 2844 (total: 11561), 24.60 %
length(levels(as.factor(browse_house$FLATEID[browse_house$disthus <= "200"]))) # 3748 (total: 11561), 32.42 %

length(levels(as.factor(browse$FLATEID[browse$distvei2 <= "200"]))) # 2844 (total: 11561), 24.60 %
length(levels(as.factor(browse$FLATEID[browse$disthus <= "200"]))) # 3748 (total: 11561), 32.42 %


## Recruitment
load("processdata/recruits_house_2021_02_02.rda")
length(levels(as.factor(recruits$FLATEID[recruits$distvei2 <= "200"]))) # 2602 (total: 10547), 24.67 %
length(levels(as.factor(recruits$FLATEID[recruits$disthus_600 <= "200"]))) # 662 (total: 10547), 6.28 %

length(levels(as.factor(recruits$FLATEID[recruits$distvei2 <= "200"]))) # 2602 (total: 10547), 24.67 %
length(levels(as.factor(recruits$FLATEID[recruits$disthus_600 <= "200"]))) # 662 (total: 10547), 6.28 %


```




## correlation plot explanatory variables
```{r}
library(ggplot2)
library(GGally)

## Browsing pressure
# house
ggcorr(browse_house, nbreaks = 6, label = T, low = "red3", high = "green3",  
       label_round = 2, name = "Correlation Scale", label_alpha = T, hjust = 0.75) +
  ggtitle(label = "Correlation Plot") +
  theme(plot.title = element_text(hjust = 0.6))

# road
ggcorr(browse_roads, nbreaks = 6, label = T, low = "red3", high = "green3",  
       label_round = 2, name = "Correlation Scale", label_alpha = T, hjust = 0.75) +
  ggtitle(label = "Correlation Plot") +
  theme(plot.title = element_text(hjust = 0.6))




## Recruits
# house
ggcorr(recruits_house, use = "pearson", nbreaks = 6, label = T, low = "red3", high = "green3",  
       label_round = 2, name = "Correlation Scale", label_alpha = T, hjust = 0.75) +
  ggtitle(label = "Correlation Plot") +
  theme(plot.title = element_text(hjust = 0.6))

# road
ggcorr(recruits_roads, use = "pearson", nbreaks = 6, label = T, low = "red3", high = "green3", label_round = 2, name = "Correlation Scale", label_alpha = T, hjust = 0.75) +
  ggtitle(label = "Correlation Plot") +
  theme(plot.title = element_text(hjust = 0.6))





```




## correlation ungskogspleie (or similar) and distances
```{r}

load("rawdata/browse0.1.rda")
ggcorr(data = NULL, cor_matrix = cor(browse0.1[, c(84, 103, 105)], use = "complete.obs"), method = "pearson", nbreaks = 6, label = T, low = "red3", high = "green3",  
       label_round = 1, label_alpha = T, hjust = 0.75) +
  ggtitle(label = "") +
  theme(plot.title = element_text(hjust = 0.6))

cor_matrix <- browse0.1[, c(84, 103, 105)]
cor(cor_matrix, use = "complete.obs")

cor.test(browse0.2_ung$ungskogspleie, browse0.2_ung$disthuskat_600)


ggplot(browse0.1, aes(ungskog)) +
  geom_histogram()
ggplot(browse0.1, aes(disthus)) +
  geom_histogram()

ggplot(browse0.1, aes(disthus, color = ungskog))
  geom_histogram()


load("processdata/browse0.2_ung.rda")
names(browse0.2_ung)
browse0.2_ung <- browse0.2_ung[browse0.2_ung$takst == 9, ]

browse0.2_ung$skogkategori <- as.factor(browse0.2_ung$skogkategori)
browse0.2_ung$treartgruppe9 <- as.factor(browse0.2_ung$treartgruppe9)
browse0.2_ung$disthus_600 <- ifelse(browse0.2_ung$disthus >= 600, 600, browse0.2_ung$disthus)
browse0.2_ung$disthuskat_600 <- ifelse(browse0.2_ung$disthuskat >= 600, 600, browse0.2_ung$disthuskat)

browse0.2_ung2 <- browse0.2_ung[browse0.2_ung$ungskogspleie > 0, ]

browse0.2_ung <- browse0.2_ung[which(browse0.2_ung$skogkategori == "Hyproduktiv_ungskog" | browse0.2_ung$skogkategori == "Lavproduktiv_ungskog"), ]
table(browse0.2_ung$skogkategori)

browse0.2_ung <- browse0.2_ung[which(browse0.2_ung$treartgruppe9 == "ROS" | browse0.2_ung$treartgruppe9 == "LAUV"), ]

browse0.2_ung3 <- browse0.2_ung[which(browse0.2_ung$treartgruppe9 == "ROS"), ]
browse0.2_ung4 <- browse0.2_ung[which(browse0.2_ung$treartgruppe9 == "LAUV"), ]
table(browse0.2_ung$treartgruppe9)

summary(browse0.2_ung$ungskogspleie)




glm_ungskog <- glm(ungskogspleie ~ disthus, data = browse0.2_ung)
glm_ungskog_kat <- glm(ungskogspleie ~ disthuskat_600, data = browse0.2_ung)
glm_ungskog_kat3 <- glm(ungskogspleie ~ disthuskat_600, data = browse0.2_ung3)
glm_ungskog_kat4 <- glm(ungskogspleie ~ disthuskat_600, data = browse0.2_ung4)
# glm_ungskog2 <- glm(ungskogspleie ~ disthus_600, data = browse0.2_ung, family = binomial)
# glm_ungskog_pos <- glm(ungskogspleie ~ disthus, data = browse0.2_ung2)
glm_ungskog_kat_pos <- glm(ungskogspleie ~ disthuskat_600, data = browse0.2_ung2)


summary(glm_ungskog)
summary(glm_ungskog_kat)
summary(glm_ungskog_kat3)
summary(glm_ungskog_kat4)
# summary(glm_ungskog2)
# summary(glm_ungskog_pos)
summary(glm_ungskog_kat_pos)

library(ggplot2)
library(pscl)
pR2(glm_ungskog)

plot(glm_ungskog)

library(ggiraphExtra)
ggPredict(glm_ungskog_kat_pos, se=TRUE, interactive=TRUE, digits=3)

ggplot(browse0.2_ung, aes(disthuskat_600, ungskogspleie)) +
  stat_smooth(method = glm)
```

